---
title: "Examining BGG Rating Models"
author: Phil Henrickson
date: "`r Sys.Date()`"
output: 
  html_document:
        toc: true
        toc_depth: 3
        keep_md: true
---

```{r global settings, echo=F, warning=F, message=F}

knitr::opts_chunk$set(echo = F,
                      error=F,
                      dev="png",
                      fig.width = 9,
                      fig.height = 6)

options(knitr.duplicate.label = "allow")

options(scipen=999)

source("load_packages.R")
source("theme_phil.R")
library(plumber)
rm(a)

```

```{r flextable settings, echo=F, warning=F, message=F}

library(webshot2)
library(flextable)
set_flextable_defaults(theme_fun = theme_alafoli,
                       font.color = "grey10",
  padding.bottom = 6, 
  padding.top = 6,
  padding.left = 6,
  padding.right = 6,
  background.color = "white")

```

## Get Functions

```{r get function, echo=F, warning=F, message=F}

# function for loading game by id
source("functions/get_game_record.R")

# function for reading in current bgg data
source("functions/get_bgg_data_from_github.R")

# function for predicting with trained model
source("functions/bake_and_predict_ratings.R")

# function for predicting with stan
source("functions/bake_and_predict_posterior.R")

# function for plotting posterior
source("functions/plot_posterior.R")

# function for predicting complexity then ratings
source("functions/bake_and_predict_avgweight_and_ratings.R")

# function for renaming and tidying output
rename_func<-function(x) {
  
  x<-gsub("cat_memory", "cat_memory_game", x)
  x<-gsub("cat_spiessecret_agents", "cat_spies_secret_agents", x)
 # x<-gsub("number_artists", "number_top_artists", x)
  x<-gsub("cat_","", x)
  x<-gsub("mech_","", x)
  x<-gsub("pub_","", x)
  x<-gsub("des_","", x)
  x<-gsub("art_", "Artist ", x)
  x<-gsub("avgweight", "Average Weight", x)
  x<-gsub("yearpublished", "Year Published", x)
  x<-gsub("minage", "Min Age", x)
  x<-gsub("playingtime", "Playing Time", x)
  x<-gsub("maxplayers", "Max Players", x)
  x<-gsub("minplayers", "Min Players", x)
  x<-gsub("murdermystery", "murder mystery", x)
  x<-gsub("_", " ", x)
  
  str_to_title(x)

}

# geek rating
baverage_func<- function(x) {
        
        breaks = seq(5.5, 8.3, 0.1)
        colorRamp=colorRampPalette(c("white", "deepskyblue1"))
        col_palette <- colorRamp(length(breaks))
        mycut <- cut(x, 
                     breaks = breaks,
                     include.lowest = TRUE, 
                     right=T,
                     label = FALSE)
        col_palette[mycut]
        
}

# avg rating
average_func<- function(x) {
        
        breaks = seq(6.5, 9.9, 0.1)
        colorRamp=colorRampPalette(c("white", "deepskyblue1"))
        col_palette <- colorRamp(length(breaks))
        mycut <- cut(x, 
                     breaks = breaks,
                     include.lowest = TRUE, 
                     right=T,
                     label = FALSE)
        col_palette[mycut]
        
}

# avgweight
avgweight_func<- function(x) {
  
  breaks<-seq(1, 5, 0.1)
#  breaks = weight_deciles
  colorRamp=colorRampPalette(c("white", "red"))
  col_palette <- colorRamp(length(breaks))
  mycut <- cut(x, 
    breaks = breaks,
    include.lowest = TRUE, 
    right=T,
    label = FALSE)
  col_palette[mycut]
  
}

```

```{r get todays bgg data then filter to year, echo=F, warning=F, message=F}

# get todays data from bgg
bgg_today<-get_bgg_data_from_github(Sys.Date())

```

Push through function

## Estimating Ratings

These estimates make use of the current avgweight on BGG. For games with relatively few votes, the avgweight might be unreliable. In the next section, I first estimate the avgweight and then use the estimated value in the model.

### 2020

```{r predict ratings for 2020, echo=F, warning=F, message=F}


# Predict BGG ratings and complexity with previously trained models.

# pull ids
ids = bgg_today %>%
  filter(game_release_year == 2020) %>%
  pull(game_id)

# feed through predictive models to get predictions
preds = bake_and_predict_ratings(ids,
                                         "xgbTree_fit")

```

```{r now create a table for 2020, warning=F, message=F}

# ratings
ratings = preds$estimate

# combine
table = ratings %>%
        spread(outcome, pred) %>%
  mutate(method = gsub("_fit", "", method)) %>%
        arrange(desc(baverage))

# edit
tidy_table = table %>%
        arrange(desc(baverage)) %>%
        mutate(Row = row_number()) %>%
        mutate(yearpublished = as.character(yearpublished),
               game_id = as.character(game_id)) %>%
        rename(Published = yearpublished,
               BGG_ID = game_id,
               Game = name) %>%
        select(Row, BGG_ID, Published, Game, average, baverage)

# get to ft
ft_table = tidy_table %>%
        flextable() %>%
        flextable::autofit() %>%
        flextable::align(j = c("average", "baverage"),
                         align = "center",
                         part = "all") %>%
        add_header(average = "Estimated",
                   baverage = "Estimated", 
                   top = TRUE) %>%
        merge_h(part = "header") %>%
        add_footer(top = F, values = paste("Predictions as of ", Sys.Date())) %>%
        bold(part = "header") %>%
        border_remove() %>%
        bg(., j = c("baverage"),
           bg = baverage_func) %>%
        bg(., j = c("average"),
                   bg = average_func) %>%
  set_caption("Estimates of BGG Ratings for Upcoming Games")

# display
ft_table

```


### 2021

```{r predict ratings for 2021, echo=F, warning=F, message=F}

# Predict BGG ratings and complexity with previously trained models.

# pull ids
ids = bgg_today %>%
  filter(game_release_year == 2021) %>%
  pull(game_id)

# feed through predictive models to get predictions
preds = bake_and_predict_ratings(ids,
                                         "xgbTree_fit")

```

```{r now create a table for 2021, echo=F, warning=F, message=F}

# ratings
ratings = preds$estimate

# combine
table = ratings %>%
        spread(outcome, pred) %>%
  mutate(method = gsub("_fit", "", method)) %>%
        arrange(desc(baverage))

# edit
tidy_table = table %>%
        arrange(desc(baverage)) %>%
        mutate(Row = row_number()) %>%
        mutate(yearpublished = as.character(yearpublished),
               game_id = as.character(game_id)) %>%
        rename(Published = yearpublished,
               BGG_ID = game_id,
               Game = name) %>%
        select(Row, BGG_ID, Published, Game, average, baverage)

# get to ft
ft_table = tidy_table %>%
        flextable() %>%
        flextable::autofit() %>%
        flextable::align(j = c("average", "baverage"),
                         align = "center",
                         part = "all") %>%
        add_header(average = "Estimated",
                   baverage = "Estimated", 
                   top = TRUE) %>%
        merge_h(part = "header") %>%
        add_footer(top = F, values = paste("Predictions as of ", Sys.Date())) %>%
        bold(part = "header") %>%
        border_remove() %>%
        bg(., j = c("baverage"),
           bg = baverage_func) %>%
        bg(., j = c("average"),
                   bg = average_func) %>%
  set_caption("Estimates of BGG Ratings for Upcoming Games")

# display
ft_table

```


### 2022

```{r predict ratings for 2022, echo=F, warning=F, message=F}

# Predict BGG ratings and complexity with previously trained models.

# pull ids
ids = bgg_today %>%
  filter(game_release_year == 2022) %>%
  pull(game_id)

# feed through predictive models to get predictions
preds = bake_and_predict_ratings(ids,
                                         "xgbTree_fit")

```

```{r now create a table for 2022, echo=F, warning=F, message=F}

# ratings
ratings = preds$estimate

# combine
table = ratings %>%
        spread(outcome, pred) %>%
  mutate(method = gsub("_fit", "", method)) %>%
        arrange(desc(baverage))

# edit
tidy_table = table %>%
        arrange(desc(baverage)) %>%
        mutate(Row = row_number()) %>%
        mutate(yearpublished = as.character(yearpublished),
               game_id = as.character(game_id)) %>%
        rename(Published = yearpublished,
               BGG_ID = game_id,
               Game = name) %>%
        select(Row, BGG_ID, Published, Game, average, baverage)

# get to ft
ft_table = tidy_table %>%
        flextable() %>%
        flextable::autofit() %>%
        flextable::align(j = c("average", "baverage"),
                         align = "center",
                         part = "all") %>%
        add_header(average = "Estimated",
                   baverage = "Estimated", 
                   top = TRUE) %>%
        merge_h(part = "header") %>%
        add_footer(top = F, values = paste("Predictions as of ", Sys.Date())) %>%
        bold(part = "header") %>%
        border_remove() %>%
        bg(., j = c("baverage"),
           bg = baverage_func) %>%
        bg(., j = c("average"),
                   bg = average_func) %>%
  set_caption("Estimates of BGG Ratings for Upcoming Games")

# display
ft_table

```

## Estimating Weight and Ratings

These models first estimate the weight of the game, then predict the average rating and geek rating.

### 2020

```{r get games and predict both outcomes 2020, echo=F, warning=F, message=F}

# Predict BGG ratings and complexity with previously trained models.
# pull ids
ids = bgg_today %>%
  filter(game_release_year == 2020) %>%
  pull(game_id)

# feed through predictive models to get predictions
preds = bake_and_predict_avgweight_and_ratings(ids,
                                         "xgbTree_fit")

# estimated weight
complexity = preds$estimated_weight
ratings = preds$estimated_rating

# combine
table = ratings %>%
        spread(outcome, pred) %>%
        select(-method) %>%
        left_join(., 
                  complexity %>%
                          spread(outcome, pred) %>%
                          select(game_id, avgweight),
                  by = "game_id") %>%
        arrange(desc(baverage))

```

```{r create flextable for both estimates for 2020, echo=F, warning=F, message=F}

# edit
tidy_table = table %>%
        arrange(desc(baverage)) %>%
        mutate(Row = row_number()) %>%
        mutate(yearpublished = as.character(yearpublished),
               game_id = as.character(game_id)) %>%
        rename(Published = yearpublished,
               BGG_ID = game_id,
               Game = name) %>%
        select(Row, BGG_ID, Published, Game, average, baverage, avgweight)

# get to ft
ft_table = tidy_table %>%
        flextable() %>%
        flextable::autofit() %>%
        flextable::align(j = c("average", "baverage", "avgweight"),
                         align = "center",
                         part = "all") %>%
        add_header(average = "Estimated",
                   baverage = "Estimated", 
                   avgweight = "Estimated",
                   top = TRUE) %>%
        merge_h(part = "header") %>%
        add_footer(top = F, values = paste("Predictions as of ", Sys.Date())) %>%
        bold(part = "header") %>%
        border_remove() %>%
        bg(., j = c("baverage"),
           bg = baverage_func) %>%
        bg(., j = c("average"),
                   bg = average_func) %>%
       bg(., j = c("avgweight"),
           bg = avgweight_func) %>%
  set_caption("Estimates of BGG Ratings for Upcoming Games")

# display
ft_table

```


### 2021

```{r get games and predict both outcomes 2021, echo=F, warning=F, message=F}

# Predict BGG ratings and complexity with previously trained models.
# pull ids
ids = bgg_today %>%
  filter(game_release_year == 2021) %>%
  pull(game_id)

# feed through predictive models to get predictions
preds = bake_and_predict_avgweight_and_ratings(ids,
                                         "xgbTree_fit")

# estimated weight
complexity = preds$estimated_weight
ratings = preds$estimated_rating

# combine
table = ratings %>%
        spread(outcome, pred) %>%
        select(-method) %>%
        left_join(., 
                  complexity %>%
                          spread(outcome, pred) %>%
                          select(game_id, avgweight),
                  by = "game_id") %>%
        arrange(desc(baverage))

```

```{r create flextable for both estimates for 2021, warning=F, message=F}

# edit
tidy_table = table %>%
        arrange(desc(baverage)) %>%
        mutate(Row = row_number()) %>%
        mutate(yearpublished = as.character(yearpublished),
               game_id = as.character(game_id)) %>%
        rename(Published = yearpublished,
               BGG_ID = game_id,
               Game = name) %>%
        select(Row, BGG_ID, Published, Game, average, baverage, avgweight)

# get to ft
ft_table = tidy_table %>%
        flextable() %>%
        flextable::autofit() %>%
        flextable::align(j = c("average", "baverage", "avgweight"),
                         align = "center",
                         part = "all") %>%
        add_header(average = "Estimated",
                   baverage = "Estimated", 
                   avgweight = "Estimated",
                   top = TRUE) %>%
        merge_h(part = "header") %>%
        add_footer(top = F, values = paste("Predictions as of ", Sys.Date())) %>%
        bold(part = "header") %>%
        border_remove() %>%
        bg(., j = c("baverage"),
           bg = baverage_func) %>%
        bg(., j = c("average"),
                   bg = average_func) %>%
       bg(., j = c("avgweight"),
           bg = avgweight_func) %>%
  set_caption("Estimates of BGG Ratings for Upcoming Games")

# display
ft_table

```


### 2022

```{r get games and predict both outcomes 2022, echo=F, warning=F, message=F}

# Predict BGG ratings and complexity with previously trained models.
# pull ids
ids = bgg_today %>%
  filter(game_release_year == 2022) %>%
  pull(game_id)

# feed through predictive models to get predictions
preds = bake_and_predict_avgweight_and_ratings(ids,
                                         "xgbTree_fit")

# estimated weight
complexity = preds$estimated_weight
ratings = preds$estimated_rating

# combine
table = ratings %>%
        spread(outcome, pred) %>%
        select(-method) %>%
        left_join(., 
                  complexity %>%
                          spread(outcome, pred) %>%
                          select(game_id, avgweight),
                  by = "game_id") %>%
        arrange(desc(baverage))

```

```{r create flextable for both estimates for 2022, warning=F, message=F}

# edit
tidy_table = table %>%
        arrange(desc(baverage)) %>%
        mutate(Row = row_number()) %>%
        mutate(yearpublished = as.character(yearpublished),
               game_id = as.character(game_id)) %>%
        rename(Published = yearpublished,
               BGG_ID = game_id,
               Game = name) %>%
        select(Row, BGG_ID, Published, Game, average, baverage, avgweight)

# get to ft
ft_table = tidy_table %>%
        flextable() %>%
        flextable::autofit() %>%
        flextable::align(j = c("average", "baverage", "avgweight"),
                         align = "center",
                         part = "all") %>%
        add_header(average = "Estimated",
                   baverage = "Estimated", 
                   avgweight = "Estimated",
                   top = TRUE) %>%
        merge_h(part = "header") %>%
        add_footer(top = F, values = paste("Predictions as of ", Sys.Date())) %>%
        bold(part = "header") %>%
        border_remove() %>%
        bg(., j = c("baverage"),
           bg = baverage_func) %>%
        bg(., j = c("average"),
                   bg = average_func) %>%
       bg(., j = c("avgweight"),
           bg = avgweight_func) %>%
  set_caption("Estimates of BGG Ratings for Upcoming Games")

# display
ft_table

```




