---
title: "Predicting Reviewer Ratings and Collections"
author: Phil Henrickson
date: "`r Sys.Date()`"
output: 
  html_document:
        toc: true
        toc_depth: 3
        keep_md: true
    
---

This notebook is for building predictive models of boardgame ratings for individal users.

```{r global seetings, echo=F, warning=F, message=F}

knitr::opts_chunk$set(echo = F,
                      dev="png",
                      fig.width = 8,
                      fig.height = 6)

options(knitr.duplicate.label = "allow")

options(scipen=999)

```

```{r load and set packages, warning=F, message=F, include=FALSE, results = 'hide'}

source("load_packages.R")
source("theme_phil.R")
library(webshot2)

```

```{r flextable settings}

library(magick)
library(flextable)
set_flextable_defaults(theme_fun = theme_booktabs,
                       font.color = "grey10",
  padding.bottom = 6, 
  padding.top = 6,
  padding.left = 6,
  padding.right = 6,
  background.color = "white")

```

## Connect to Big Query

### Active Game Rankings

We'll first connect to the most recent day of BGG data that we have in our database. These are the active rankings of games - where they stand in the BGG database as of the most recent load, which I usually update once a week.

```{r connect to big query}

library(bigrquery)

# get project credentials
PROJECT_ID <- "gcp-analytics-326219"
BUCKET_NAME <- "test-bucket"


# establish connection
bigquerycon<-dbConnect(
        bigrquery::bigquery(),
        project = PROJECT_ID,
        dataset = "bgg"
)

# query table
active_games<-DBI::dbGetQuery(bigquerycon, 
                              'SELECT * FROM bgg.active_games_daily')


my_caption = list(labs(caption = paste(paste("Data from boardgamegeek.com as of", max(as.Date(active_games$timestamp))),
                        paste("Data and analysis at github.com/phenrickson/bgg"), sep="\n")))

```

### Additional Game Information

We also want to pull down other tables containing the information that we know about games.

```{r query tables with game information}

# general game info
games_info<-DBI::dbGetQuery(bigquerycon, 
                              'SELECT * FROM bgg.active_games_info')

# game categories
game_categories<-DBI::dbGetQuery(bigquerycon, 
                              'SELECT 
                              a.game_id,
                              b.category_id,
                              b.category
                              FROM bgg.game_categories a
                               LEFT JOIN bgg.category_ids b 
                               ON a.category_id = b.category_id')

# game mechanics
game_mechanics<-DBI::dbGetQuery(bigquerycon, 
                              'SELECT 
                              a.game_id,
                              b.mechanic_id,
                              b.mechanic
                              FROM bgg.game_mechanics a
                               LEFT JOIN bgg.mechanic_ids b 
                               ON a.mechanic_id = b.mechanic_id')

# game publishers
game_publishers<-DBI::dbGetQuery(bigquerycon, 
                              'SELECT 
                              a.game_id,
                              b.publisher_id,
                              b.publisher
                              FROM bgg.game_publishers a
                               LEFT JOIN bgg.publisher_ids b 
                               ON a.publisher_id = b.publisher_id')

# game designers
game_designers<-DBI::dbGetQuery(bigquerycon, 
                              'SELECT 
                              a.game_id,
                              b.designer_id,
                              b.designer
                              FROM bgg.game_designers a
                               LEFT JOIN bgg.designer_ids b 
                               ON a.designer_id = b.designer_id')

# game artists
game_artists<-DBI::dbGetQuery(bigquerycon, 
                              'SELECT 
                              a.game_id,
                              b.artist_id,
                              b.artist
                              FROM bgg.game_artists a
                               LEFT JOIN bgg.artist_ids b 
                               ON a.artist_id = b.artist_id')

```

## Exploratory Analysis

Now we'll grab the collections data for bgg users that we're tracking.

```{r get collections, warning=F}

# # game collections
# game_collections_raw<-DBI::dbGetQuery(bigquerycon, 
#                               'SELECT 
#                               *
#                               FROM bgg.historical_collections 
#                               WHERE date = (SELECT max(date) FROM bgg.historical_collections)')

# load bgg analytics
library(bggAnalytics)

# load function for grabbing collections
source("functions/get_collection.R")

# use function for specified users
users<-c("mrbananagrabber",
         "Quinns",
         "TomVasel",
         "ZeeGarcia",
         "rahdo",
         "Watch%20It%20Played",
         "NoPunIncluded",
         "Gyges")
         
```


```{r try loading collections}
# loop and combine

game_collections_raw<-foreach(i = 1:length(users), .combine = rbind.data.frame) %do% {
                
  Sys.sleep(3)
  
  get_collection(users[i]) %>%
                as_tibble()
        
}

```


```{r clean up collections}

# find duplicates
dupe_rows = seq(1:nrow(game_collections_raw))[duplicated(game_collections_raw)]
                
# remove duplicates
game_collections = game_collections_raw[-dupe_rows,]

# add in game info
collection_info <- game_collections %>%
  left_join(., games_info,
            by = c("game_id")) %>%
  mutate(username = case_when(username == 'Watch%20It%20Played' ~ 'Watch_It_Played',
                              TRUE ~ username))

# confirm no duplicates
table(duplicated(collection_info))

```

We can look at these collections.

```{r examine collections}

# size
collection_info %>%
  filter(username != 'mrbananagrabber') %>%
  filter(!is.na(yearpublished)) %>%
  filter(!is.na(name)) %>%
  group_by(username) %>%
  summarize(games_in_collection = sum(own)) %>%
  ggplot(., aes(x = games_in_collection,
                y=reorder(username, games_in_collection)))+
  geom_col()+
  theme_phil()+
  ylab("bgg_username")+
  xlab("Number of Games in Collection")+
  my_caption

```

We care about two different outcomes: first, does a user own a game? If it it's in their collection (or previously has been in their collection), we can classify it as a yes, a purchase. 

Second, we also have a continuous measure of ratings for each game. If we plot the ratings for each of these users, we can see how differently the distributions are for different users.

```{r look at ratings for each game, warning=F, message=F}

set.seed(199)

# density
collection_info %>%
  filter(username != 'mrbananagrabber') %>%
    filter(!is.na(yearpublished)) %>%
  filter(!is.na(name)) %>%
  filter(!is.na(rating)) %>%
  group_by(username) %>%
  mutate(median_rating = median(rating)) %>%
  mutate(name = abbreviate(name, minlength=25)) %>%
  ggplot(., aes(x = rating,
          #      fill = username,
                label = name,
                y=reorder(username, median_rating)))+
  geom_density_ridges(quantile_lines=TRUE,
                   #   fill = 'grey60',
                      alpha=0.5,
                      quantile_fun=function(x,...)mean(x))+
  ylab("bgg_username")+
  theme_phil()+
  xlab("User Game Rating")+
  scale_fill_colorblind()+
  guides(fill = "none")+
  my_caption


# ratings
collection_info %>%
  filter(!is.na(yearpublished)) %>%
  filter(!is.na(name)) %>%
  filter(!is.na(rating)) %>%
  group_by(username) %>%
  mutate(median_rating = median(rating)) %>%
  mutate(name = abbreviate(name, minlength=25)) %>%
  ggplot(., aes(x = rating,
            #    color = username,
                label = name,
                y=reorder(username, median_rating)))+
  geom_jitter(alpha=0.1,
              width=0.4,
              size = 0.5,
              height = 0.1)+
  geom_text(check_overlap = T,
            size = 2,
            position=position_jitter(width=0.4,height=0.2))+
  theme_phil()+
  geom_boxplot(alpha = 0.5,
               outlier.shape = NA)+
  ylab("bgg_username")+
  xlab("User Game Rating")+
  scale_color_colorblind()+
  guides(color = "none")+
  my_caption


```

Here's the thing though: TomVasel has seemingly stoppped updating his ownership as of 2018, same for NoPunIncluded.

```{r look at owned}

collection_info %>%
  filter(yearpublished > 2010 & yearpublished < 2022) %>%
  group_by(yearpublished, username) %>%
  summarize(n_owned = sum(own),
            n_rated = n_distinct(game_id),
            .groups = 'drop') %>%
  melt(., id.vars = c("yearpublished", "username")) %>%
  ggplot(., aes(x=yearpublished, y=value, color = variable, by = username))+
  geom_line()+
  facet_wrap(username~.,
             scales="free_y")+
  theme_phil()+
  scale_color_colorblind()+
  my_caption

```

Alright so it would seem that NoPunIncluded stoppped updating their BGG account after 2015, and that TomVasel has continued to rate games but he no logner lists that he owns them. Bleah.

So, that means we can probably toss out NoPunIncluded and not be missing too much, but for TomVasel we might need to create a whole new category. Let's look at the games he's rated by whether he owns them, filtering to games published before 2017.

```{r tom vasels collection}

collection_info %>%
    filter(!is.na(yearpublished)) %>%
  filter(!is.na(name)) %>%
  filter(yearpublished < 2017) %>%
  filter(username == 'TomVasel') %>%
  mutate(own = case_when(own == 1 ~ 'yes',
                         TRUE ~ 'no')) %>%
  ggplot(., aes(x=rating,
                fill = own,
                y =own))+
  geom_density_ridges(alpha=0.8,
                      color = 'white',
                      quantile_lines=TRUE, quantiles=2)+
  facet_wrap(username~.)+
  theme_phil()+
  scale_fill_manual(values = c("grey60", "navy"))+
  my_caption

```

So the median rating for games he owns is 8, as opposed to 6 for games he doesn't. If we make the assumption that he owns above an 8 for games published in 2018 and 2019, what do games would we consider him owning.

```{r look at games he rates highly as likely owned}

collection_info %>%
    filter(!is.na(yearpublished)) %>%
  filter(!is.na(name)) %>%
  filter(yearpublished > 2017 & yearpublished < 2020) %>%
  filter(username == 'TomVasel') %>%
  mutate(own = case_when(own == 1 ~ 'yes',
                         TRUE ~ 'no')) %>%
  filter(rating >= 8) %>%
  left_join(., games_info) %>%
  select(username, yearpublished, game_id, name, rating, own)

```

We'll roll with that as a rule for TomVasel, considering games above 8 after these years as a likely own.


```{r owned by complexity, warning=F, message=F}

# # complexity with me
# collection_info %>%
#   filter(!is.na(yearpublished)) %>%
#   filter(!is.na(name)) %>%
#   filter(own == 1 | prevowned == 1) %>%
#   mutate(name = abbreviate(name, minlength=25)) %>%
#   group_by(username) %>%
#   mutate(median_weight = median(avgweight, na.rm=T)) %>%
#   ggplot(., aes(x = avgweight,
#                 label = name,
#                 fill = username,
#                 y = reorder(username, median_weight)))+
#   geom_density_ridges(quantile_lines=TRUE,
#                     #  fill = 'grey60',
#                       alpha=0.6,
#                       quantile_fun=function(x,...)mean(x))+
#   ylab("bgg_username")+
#   theme_phil()+
#   scale_fill_colorblind()+
#   guides(fill = "none")

# without me
collection_info %>%
    mutate(own = case_when(username == 'TomVasel' & rating >= 8 ~ 1,
                         TRUE ~ own)) %>%
   filter(!is.na(yearpublished)) %>%
  filter(!is.na(name)) %>%
  filter(own == 1 | prevowned == 1) %>%
  filter(yearpublished > 1980) %>%
  filter(yearpublished < 2020) %>%
  mutate(name = abbreviate(name, minlength=25)) %>%
  group_by(username) %>%
  mutate(median_weight = median(avgweight, na.rm=T)) %>%
  ggplot(., aes(x = avgweight,
                label = name,
                fill = username,
                y = reorder(username, median_weight)))+
  geom_density_ridges(quantile_lines=TRUE,
                    #  fill = 'grey60',
                      alpha=0.6,
                      quantile_fun=function(x,...)mean(x))+
  ylab("bgg_username")+
  xlab("Average Game Weight on BGG")+
  theme_phil()+
  scale_fill_colorblind()+
  guides(fill = "none")+
  my_caption

```

Games owned by yearpublished

```{r yearpublished of collection, warning=F, message=F}

# collection by yearpublished
# collection_info %>%
#   filter(!is.na(yearpublished)) %>%
#   filter(!is.na(name)) %>%
#   filter(own == 1 | prevowned == 1) %>%
#   filter(yearpublished > 1980) %>%
#   mutate(name = abbreviate(name, minlength=25)) %>%
#   group_by(username) %>%
#   mutate(median_year = median(yearpublished, na.rm=T)) %>%
#   ggplot(., aes(x = yearpublished,
#                 label = name,
#                 fill = username,
#                 y = reorder(username, median_year)))+
#   geom_density_ridges(quantile_lines=TRUE,
#                     #  fill = 'grey60',
#                       alpha=0.6,
#                       quantile_fun=function(x,...)mean(x))+
#   ylab("bgg_username")+
#   xlab("Year Published")
#   theme_phil()+
#   scale_fill_colorblind()+
#   guides(fill = "none")+
#       labs(caption = paste('Data from boardgamegeek.com as of', max(collection_info$date), 
#                           '\n',
#                           'Analysis and code from github.com/phenrickson/bgg'))+
#   theme(plot.caption = element_text(size=8))

# collection by yearpublished without me
collection_info %>%
      mutate(own = case_when(username == 'TomVasel' & rating >= 8 ~ 1,
                         TRUE ~ own)) %>%
 # filter(username != 'mrbananagrabber') %>%
  filter(!is.na(yearpublished)) %>%
  filter(!is.na(name)) %>%
  filter(own == 1) %>%
  filter(yearpublished > 1980) %>%
  filter(yearpublished < 2020) %>%
  mutate(name = abbreviate(name, minlength=25)) %>%
  group_by(username) %>%
  mutate(median_year = median(yearpublished, na.rm=T)) %>%
  ggplot(., aes(x = yearpublished,
                label = name,
                fill = username,
                y = reorder(username, median_year)))+
  geom_density_ridges(quantile_lines=TRUE,
                    #  fill = 'grey60',
                      alpha=0.6,
                      quantile_fun=function(x,...)mean(x))+
  ylab("bgg_username")+
  xlab("Year Published")+
  theme_phil()+
  scale_fill_colorblind()+
  guides(fill = "none")+
  my_caption

```

Geek rating of collection

```{r collection by geek rating, warning=F}

# # geek rating
# collection_info %>%
#   left_join(., active_games %>%
#               select(game_id, baverage, average),
#             by = "game_id") %>%
#   filter(!is.na(yearpublished)) %>%
#   filter(!is.na(name)) %>%
#   filter(own == 1 | prevowned == 1) %>%
#   group_by(username) %>%
#   mutate(median_baverage = median(baverage, na.rm = T)) %>%
#   mutate(name = abbreviate(name, minlength=25)) %>%
#   ggplot(., aes(x = baverage,
#                 label = name,
#                 fill = username,
#                 y = reorder(username, median_baverage)))+
#   geom_density_ridges(quantile_lines=TRUE,
#                     #  fill = 'grey60',
#                       alpha=0.6,
#                       quantile_fun=function(x,...)mean(x))+
#   ylab("bgg_username")+
#   theme_phil()+
#   scale_fill_colorblind()+
#   guides(fill = "none")

# geek rating
collection_info %>%
  left_join(., active_games %>%
              select(game_id, baverage, average),
            by = "game_id") %>%
#  filter(username != 'mrbananagrabber') %>%
  filter(!is.na(yearpublished)) %>%
  filter(!is.na(name)) %>%
  filter(yearpublished < 2020) %>%
      mutate(own = case_when(username == 'TomVasel' & rating >= 8 ~ 1,
                         TRUE ~ own)) %>%
  filter(own == 1) %>%
  group_by(username) %>%
  mutate(median_baverage = median(baverage, na.rm = T)) %>%
  mutate(name = abbreviate(name, minlength=25)) %>%
  ggplot(., aes(x = baverage,
                label = name,
                fill = username,
                y = reorder(username, median_baverage)))+
  geom_density_ridges(quantile_lines=TRUE,
                    #  fill = 'grey60',
                      alpha=0.6,
                      quantile_fun=function(x,...)mean(x))+
  ylab("bgg_username")+
  theme_phil()+
  scale_fill_colorblind()+
  guides(fill = "none")+
  xlab("Geek Rating")+
  my_caption
# # geek rating
# collection_info %>%
#   left_join(., active_games %>%
#               select(game_id, average, average),
#             by = "game_id") %>%
#   filter(username != 'mrbananagrabber') %>%
#   filter(own == 1) %>%
#   group_by(username) %>%
#   mutate(median_average = median(average, na.rm = T)) %>%
#   mutate(name = abbreviate(name, minlength=25)) %>%
#   ggplot(., aes(x = average,
#                 label = name,
#                 fill = username,
#                 y = reorder(username, median_average)))+
#   geom_density_ridges(quantile_lines=TRUE,
#                     #  fill = 'grey60',
#                       alpha=0.6,
#                       quantile_fun=function(x,...)mean(x))+
#   ylab("bgg_username")+
#   theme_phil()+
#   scale_fill_colorblind()+
#   guides(fill = "none")

```

We can see how they each rate games vs features of the game, such as complexity.

```{r weight vs rating, warning=F, message=F, fig.height=8}

# ratings including me
# collection_info %>%
#   filter(!is.na(rating)) %>%
#   group_by(username) %>%
#   mutate(median_rating = median(rating)) %>%
#   mutate(name = abbreviate(name, minlength=25)) %>%
#   ggplot(., aes(x = avgweight,
#                 y = rating,
#                 label = name))+
#   geom_jitter(alpha=0.5,
#               width=0.4,
#               size = 0.5,
#               height = 0.1)+
#   theme_phil()+
#   facet_wrap(username ~.)+
#   stat_cor(p.accuracy = 0.01,
#            col = 'blue')+
#   # geom_text(check_overlap=T,
#   #           size = 2,
#   #           position=position_jitter(width=0.4,height=0.2))+
#   geom_smooth(method = 'lm',
#               formula = 'y ~ x')+
#   xlab("Game Complexity")+
#   ylab("User Rating")+
#     labs(caption = paste('Data from boardgamegeek.com as of', max(collection_info$date), 
#                           '\n',
#                           'Analysis and code from github.com/phenrickson/bgg'))+
#   theme(plot.caption = element_text(size=8))

# ratings without me
collection_info %>%
    filter(yearpublished < 2020) %>%
      mutate(own = case_when(username == 'TomVasel' & rating >= 8 ~ 1,
                         TRUE ~ own)) %>%
 # filter(username != 'mrbananagrabber') %>%
  filter(!is.na(rating)) %>%
  group_by(username) %>%
  mutate(median_rating = median(rating)) %>%
  mutate(name = abbreviate(name, minlength=25)) %>%
  ggplot(., aes(x = avgweight,
                y = rating,
                label = name))+
  geom_jitter(alpha=0.5,
              width=0.4,
              size = 0.5,
              height = 0.1)+
  theme_phil()+
  facet_wrap(username ~.)+
  stat_cor(p.accuracy = 0.01,
           col = 'blue')+
  # geom_text(check_overlap=T,
  #           size = 2,
  #           position=position_jitter(width=0.4,height=0.2))+
  geom_smooth(method = 'lm',
              formula = 'y ~ x')+
  xlab("Game Complexity")+
  ylab("User Rating")+
  my_caption
        
```

How does each user compare to the geek rating?

```{r rating vs geek rating and bgg rating, warning=F, message=F, fig.height=8}

# # geek rating
# collection_info %>%
#   left_join(., active_games %>%
#               select(game_id, baverage, average),
#             by = "game_id") %>%
#   filter(!is.na(rating)) %>%
#   group_by(username) %>%
#   mutate(median_rating = median(rating)) %>%
#   mutate(name = abbreviate(name, minlength=25)) %>%
#   ggplot(., aes(x = baverage,
#                 y = rating,
#                 label = name))+
#   geom_jitter(alpha=0.5,
#               width=0.4,
#               size = 0.5,
#               height = 0.1)+
#   theme_phil()+
#   facet_wrap(username ~.)+
#   stat_cor(p.accuracy = 0.01)+
#   # geom_text(check_overlap=T,
#   #           size = 2,
#   #           position=position_jitter(width=0.4,height=0.2))+
#   geom_smooth(method = 'lm',
#               formula = 'y ~ x')+
#   xlab("Geek Rating")+
#   ylab("User Rating")+
#   labs(caption = paste('Data from boardgamegeek.com as of', max(collection_info$date), 
#                           '\n',
#                           'github.com/phenrickson/bgg'))

# baverage
collection_info %>%
  filter(yearpublished < 2020) %>%
#  filter(username != 'mrbananagrabber') %>%
  left_join(., active_games %>%
              select(game_id, baverage, average),
            by = "game_id") %>%
  filter(!is.na(rating)) %>%
  group_by(username) %>%
  mutate(median_rating = median(rating)) %>%
  mutate(name = abbreviate(name, minlength=25)) %>%
  ggplot(., aes(x = baverage,
                y = rating,
                label = name))+
  geom_jitter(alpha=0.5,
              width=0.4,
              size = 0.5,
              height = 0.1)+
  theme_phil()+
  facet_wrap(username ~.)+
  stat_cor(p.accuracy = 0.01)+
  # geom_text(check_overlap=T,
  #           size = 2,
  #           position=position_jitter(width=0.4,height=0.2))+
  geom_smooth(method = 'lm',
              formula = 'y ~ x')+
  coord_cartesian(xlim = c(1, 10.1),
                  ylim = c(1, 10.1))+
  xlab("Geek Rating")+
  ylab("User Rating")+
  my_caption


# bgg average
collection_info %>%
  filter(yearpublished < 2020) %>%
#  filter(username != 'mrbananagrabber') %>%
  left_join(., active_games %>%
              select(game_id, baverage, average),
            by = "game_id") %>%
  filter(!is.na(rating)) %>%
  group_by(username) %>%
  mutate(median_rating = median(rating)) %>%
  mutate(name = abbreviate(name, minlength=25)) %>%
  ggplot(., aes(x = average,
                y = rating,
                label = name))+
  geom_jitter(alpha=0.5,
              width=0.4,
              size = 0.5,
              height = 0.1)+
  theme_phil()+
  facet_wrap(username ~.)+
  stat_cor(p.accuracy = 0.01)+
  # geom_text(check_overlap=T,
  #           size = 2,
  #           position=position_jitter(width=0.4,height=0.2))+
  geom_smooth(method = 'lm',
              formula = 'y ~ x')+
  coord_cartesian(xlim = c(1, 10.1),
                  ylim = c(1, 10.1))+
  xlab("BGG Average")+
  ylab("User Rating")+
  my_caption

```

### Differences from BGG

What games does each reviewer disagree with the community the most?

```{r get differences}

col_func<- function(x) {
  
  breaks<-seq(1, 10, by = 0.1)
#  breaks = weight_deciles
  colorRamp=colorRampPalette(c("red", "white", "deepskyblue1"))
  col_palette <- colorRamp(length(breaks))
  mycut <- cut(x, 
    breaks = breaks,
    include.lowest = TRUE, 
    right=T,
    label = FALSE)
  col_palette[mycut]
  
}

 differences = collection_info %>%
   filter(username != 'mrbananagrabber') %>%
   left_join(., active_games %>%
               select(game_id, baverage, average)) %>%
   filter(!is.na(rating)) %>%
   select(username, game_id, name, rating,  baverage, average) %>%
   mutate(diff_from_baverage = rating - baverage) %>%
  mutate(diff_from_average = rating - average) %>%
   mutate_if(is.numeric, round, 2)

```

##### Quinns

```{r quinns differences}

### Quinns

differences %>%
  filter(username == 'Quinns') %>%
  rename(geek_rating = baverage,
         bgg_rating = average,
         user_rating = rating,
         diff_from_geek = diff_from_baverage,
         diff_from_bgg = diff_from_average) %>%
  mutate(game_id = as.character(game_id)) %>%
  select(username, game_id, name, user_rating, bgg_rating, diff_from_bgg) %>%
  rename(diff = diff_from_bgg) %>%
  arrange(diff) %>%
  head(15) %>%
  flextable() %>%
  flextable::autofit() %>%
   bg(j = c('user_rating', 'bgg_rating'),
      bg = col_func) %>%
  set_caption("Top 15 games Quinns rates lower than BGG")


differences %>%
  filter(username == 'Quinns') %>%
  rename(geek_rating = baverage,
         bgg_rating = average,
         user_rating = rating,
         diff_from_geek = diff_from_baverage,
         diff_from_bgg = diff_from_average) %>%
  mutate(game_id = as.character(game_id)) %>%
  select(username, game_id, name, user_rating, bgg_rating, diff_from_bgg) %>%
  rename(diff = diff_from_bgg) %>%
  arrange(desc(diff)) %>%
  head(15) %>%
  flextable() %>%
  flextable::autofit() %>%
   bg(j = c('user_rating', 'bgg_rating'),
      bg = col_func) %>%
  set_caption("Top 15 games Quinns rates higher than BGG")


```


##### TomVasel

```{r TomVasel differences}

differences %>%
  filter(username == 'TomVasel') %>%
  rename(geek_rating = baverage,
         bgg_rating = average,
         user_rating = rating,
         diff_from_geek = diff_from_baverage,
         diff_from_bgg = diff_from_average) %>%
  mutate(game_id = as.character(game_id)) %>%
  select(username, game_id, name, user_rating, bgg_rating, diff_from_bgg) %>%
  rename(diff = diff_from_bgg) %>%
  arrange(diff) %>%
  head(15) %>%
  flextable() %>%
  flextable::autofit() %>%
   bg(j = c('user_rating', 'bgg_rating'),
      bg = col_func) %>%
  set_caption("Top 15 games TomVasel rates lower than BGG")


differences %>%
  filter(username == 'TomVasel') %>%
  rename(geek_rating = baverage,
         bgg_rating = average,
         user_rating = rating,
         diff_from_geek = diff_from_baverage,
         diff_from_bgg = diff_from_average) %>%
  mutate(game_id = as.character(game_id)) %>%
  select(username, game_id, name, user_rating, bgg_rating, diff_from_bgg) %>%
  rename(diff = diff_from_bgg) %>%
  arrange(desc(diff)) %>%
  head(15) %>%
  flextable() %>%
  flextable::autofit() %>%
   bg(j = c('user_rating', 'bgg_rating'),
      bg = col_func) %>%
  set_caption("Top 15 games TomVasel rates higher than BGG")


```

##### ZeeGarcia

```{r ZeeGarcia, warning=F}

differences %>%
  filter(username == 'ZeeGarcia') %>%
  rename(geek_rating = baverage,
         bgg_rating = average,
         user_rating = rating,
         diff_from_geek = diff_from_baverage,
         diff_from_bgg = diff_from_average) %>%
  mutate(game_id = as.character(game_id)) %>%
  select(username, game_id, name, user_rating, bgg_rating, diff_from_bgg) %>%
  rename(diff = diff_from_bgg) %>%
  arrange(diff) %>%
  head(15) %>%
  flextable() %>%
  flextable::autofit() %>%
   bg(j = c('user_rating', 'bgg_rating'),
      bg = col_func) %>%
  set_caption("Top 15 games ZeeGarcia rates lower than BGG")


differences %>%
  filter(username == 'ZeeGarcia') %>%
  rename(geek_rating = baverage,
         bgg_rating = average,
         user_rating = rating,
         diff_from_geek = diff_from_baverage,
         diff_from_bgg = diff_from_average) %>%
  mutate(game_id = as.character(game_id)) %>%
  select(username, game_id, name, user_rating, bgg_rating, diff_from_bgg) %>%
  rename(diff = diff_from_bgg) %>%
  arrange(desc(diff)) %>%
  head(15) %>%
  flextable() %>%
  flextable::autofit() %>%
   bg(j = c('user_rating', 'bgg_rating'),
      bg = col_func) %>%
  set_caption("Top 15 games ZeeGarcia rates higher than BGG")

```

##### rahdo

```{r rahod disagree}

differences %>%
  filter(username == 'rahdo') %>%
  rename(geek_rating = baverage,
         bgg_rating = average,
         user_rating = rating,
         diff_from_geek = diff_from_baverage,
         diff_from_bgg = diff_from_average) %>%
  mutate(game_id = as.character(game_id)) %>%
  select(username, game_id, name, user_rating, bgg_rating, diff_from_bgg) %>%
  rename(diff = diff_from_bgg) %>%
  arrange(diff) %>%
  head(15) %>%
  flextable() %>%
  flextable::autofit() %>%
   bg(j = c('user_rating', 'bgg_rating'),
      bg = col_func) %>%
  set_caption("Top 15 games rahdo rates lower than BGG")


differences %>%
  filter(username == 'rahdo') %>%
  rename(geek_rating = baverage,
         bgg_rating = average,
         user_rating = rating,
         diff_from_geek = diff_from_baverage,
         diff_from_bgg = diff_from_average) %>%
  mutate(game_id = as.character(game_id)) %>%
  select(username, game_id, name, user_rating, bgg_rating, diff_from_bgg) %>%
  rename(diff = diff_from_bgg) %>%
  arrange(desc(diff)) %>%
  head(15) %>%
  flextable() %>%
  flextable::autofit() %>%
   bg(j = c('user_rating', 'bgg_rating'),
      bg = col_func) %>%
  set_caption("Top 15 games rahdo rates higher than BGG")


```

##### Gyges

```{r mark bigney}

differences %>%
    filter(game_id != 23953) %>%
  filter(username == 'Gyges') %>%
  rename(geek_rating = baverage,
         bgg_rating = average,
         user_rating = rating,
         diff_from_geek = diff_from_baverage,
         diff_from_bgg = diff_from_average) %>%
  mutate(game_id = as.character(game_id)) %>%
  select(username, game_id, name, user_rating, bgg_rating, diff_from_bgg) %>%
  rename(diff = diff_from_bgg) %>%
  arrange(diff) %>%
  head(15) %>%
  flextable() %>%
  flextable::autofit() %>%
   bg(j = c('user_rating', 'bgg_rating'),
      bg = col_func) %>%
  set_caption("Top 15 games Gyges rates lower than BGG")


differences %>%
  filter(game_id != 23953) %>%
  filter(username == 'Gyges') %>%
  rename(geek_rating = baverage,
         bgg_rating = average,
         user_rating = rating,
         diff_from_geek = diff_from_baverage,
         diff_from_bgg = diff_from_average) %>%
  mutate(game_id = as.character(game_id)) %>%
  select(username, game_id, name, user_rating, bgg_rating, diff_from_bgg) %>%
  rename(diff = diff_from_bgg) %>%
  arrange(desc(diff)) %>%
  head(15) %>%
  flextable() %>%
  flextable::autofit() %>%
   bg(j = c('user_rating', 'bgg_rating'),
      bg = col_func) %>%
  set_caption("Top 15 games Gyges rates higher than BGG")

```

How do they compare to each other?

```{r plot vs each other, warning = F, message=F}

# # with me
# collection_info %>%
#   filter(!is.na(rating)) %>%
#   select(date, username, game_id, name, rating) %>%
#   pivot_wider(names_from = 'username',
#               values_from = 'rating',
#               values_fn = mean) %>%
#   select(-date, -game_id, -name) %>%
#   cor(., use="pairwise.complete") %>%
#   ggcorrplot(
#     lab = TRUE,
#     hc.order = TRUE, type = "upper",
#     outline.color = "white"
# )
# 
#   
# collection_info %>%
#   filter(!is.na(rating)) %>%
#   select(date, username, game_id, name, rating) %>%
#   pivot_wider(names_from = 'username',
#               values_from = 'rating',
#               values_fn = mean) %>%
#   select(-date, -game_id, -name) %>%
#   ggpairs(., lower = list(continuous = wrap("smooth", size = 0.75, alpha = 0.3),
#                           combo = wrap("dot_no_facet", alpha = 0.4)))+
#   theme_minimal()+
#   theme(panel.grid.major = element_blank())


# without me
collection_info %>%
  filter(username != 'mrbananagrabber') %>%
  filter(!is.na(rating)) %>%
  select(date, username, game_id, name, rating) %>%
  pivot_wider(names_from = 'username',
              values_from = 'rating',
              values_fn = mean) %>%
  select(-date, -game_id, -name) %>%
  cor(., use="pairwise.complete") %>%
  ggcorrplot(
    lab = TRUE,
    hc.order = TRUE, type = "upper",
    outline.color = "white"
)

  
collection_info %>%
  #  filter(username != 'mrbananagrabber') %>%
  filter(!is.na(rating)) %>%
  select(date, username, game_id, name, rating) %>%
  pivot_wider(names_from = 'username',
              values_from = 'rating',
              values_fn = mean) %>%
  select(-date, -game_id, -name) %>%
  ggpairs(., lower = list(continuous = wrap("smooth", size = 0.75, alpha = 0.3),
                          combo = wrap("dot_no_facet", alpha = 0.4)))+
  theme_minimal()+
  theme(panel.grid.major = element_blank())+
  my_caption


```

We can zoom in on a few of those comparisons in particular. How do Quinns and Tom Vasel compare? Looks like they really agree about Cosmic Encounter, El Grande, Memoir 44, and RoboRally. They disagree heavily on Twister, Food Chain Magnate, and Container.

```{r compare reviwers quinns vs tom vasel, warning=F, message=F}

# quinns vs tom vasel
collection_info %>%
    filter(username != 'mrbananagrabber') %>%
  filter(!is.na(rating)) %>%
  select(date, username, game_id, name, rating) %>%
  pivot_wider(names_from = 'username',
              values_from = 'rating',
              values_fn = mean) %>%
  ggplot(., aes(x=Quinns, y = TomVasel,
                label = name))+
  geom_jitter(alpha=0.5,
              width=0.4,
              size = 0.5,
              height = 0.1)+
  geom_text(check_overlap = T,
            size = 2,
            position=position_jitter(width=0.4,height=0.2))+
  theme_phil()+
  geom_smooth(method = 'lm', formula = 'y ~ x') +
  stat_cor(p.accuracy = 0.01,
           col = 'blue')+
  xlab("Quinns' Ratings")+
  ylab("TomVasel's Ratings")+
  my_caption

```

What about Quinns vs Mark Bigney? I remember listening to a podcast where they disagreed heavily about Quacks of Quedlinburg.

```{r compare reviwers quinns vs mark bigney, warning=F, message=F}

# quinns vs mark bigney
collection_info %>%
    filter(username != 'mrbananagrabber') %>%
  filter(!is.na(rating)) %>%
  select(date, username, game_id, name, rating) %>%
  pivot_wider(names_from = 'username',
              values_from = 'rating',
              values_fn = mean) %>%
  ggplot(., aes(x=Quinns, y = Gyges,
                label = name))+
  geom_jitter(alpha=0.5,
              width=0.4,
              size = 0.5,
              height = 0.1)+
  geom_text(check_overlap = T,
            size = 2,
            position=position_jitter(width=0.4,height=0.2))+
  theme_phil()+
  geom_smooth(method = 'lm', formula = 'y ~ x') +
  stat_cor(p.accuracy = 0.01,
           col = 'blue')+
  xlab("Quinns' Ratings")+
  ylab("Gyges' Ratings")+
  my_caption

```

Tom Vasel and Mark Bigney?

```{r compare reviewers mark bigney and tom vasel, warning=F, message=F}

# tom vasel vs mark bigney
collection_info %>%
    filter(username != 'mrbananagrabber') %>%
  filter(!is.na(rating)) %>%
  select(date, username, game_id, name, rating) %>%
  pivot_wider(names_from = 'username',
              values_from = 'rating',
              values_fn = mean) %>%
  ggplot(., aes(x=TomVasel, y = Gyges,
                label = name))+
  geom_jitter(alpha=0.5,
              width=0.4,
              size = 0.5,
              height = 0.1)+
  geom_text(check_overlap = T,
            size = 2,
            position=position_jitter(width=0.4,height=0.2))+
  theme_phil()+
  geom_smooth(method = 'lm', formula = 'y ~ x') +
  stat_cor(p.accuracy = 0.01,
           col = 'blue')+
  xlab("TomVasel's Ratings")+
  ylab("Gyges' Ratings")+
  my_caption

```

Tom Vasel and Zee

```{r compare reviewers zee and tom vasel, warning=F, message=F}

# tom vasel vs zee
collection_info %>%
    filter(username != 'mrbananagrabber') %>%
  filter(!is.na(rating)) %>%
  select(date, username, game_id, name, rating) %>%
  pivot_wider(names_from = 'username',
              values_from = 'rating',
              values_fn = mean) %>%
  ggplot(., aes(x=TomVasel, y = ZeeGarcia,
                label = name))+
  geom_jitter(alpha=0.5,
              width=0.4,
              size = 0.5,
              height = 0.1)+
  geom_text(check_overlap = T,
            size = 2,
            position=position_jitter(width=0.4,height=0.2))+
  theme_phil()+
  geom_smooth(method = 'lm', formula = 'y ~ x') +
  stat_cor(p.accuracy = 0.01,
           col = 'blue')+
  xlab("TomVasel's Ratings")+
  ylab("ZeeGarcia's Ratings")+
  my_caption

```

How many games have they all owned or rated?

```{r check out overlap, warning=F}

col_num_func<- function(x) {
  
  breaks<-seq(1, 8, by = 1)
#  breaks = weight_deciles
  colorRamp=colorRampPalette(c("white", "royalblue"))
  col_palette <- colorRamp(length(breaks))
  mycut <- cut(x, 
    breaks = breaks,
    include.lowest = TRUE, 
    right=T,
    label = FALSE)
  col_palette[mycut]
  
}

collection_pivot = collection_info %>%
  mutate(own = case_when(username == 'TomVasel' & rating >= 8 ~ 1,
                         TRUE ~ own)) %>%
  filter(!is.na(yearpublished)) %>%
  filter(!is.na(name)) %>%
  filter(username != 'mrbananagrabber') %>%
  mutate(have_owned = case_when(own == 1 | prevowned == 1 | (username == 'Quinns' & !is.na(rating)) ~ 1,
                                TRUE ~ 0)) %>%
  select(yearpublished, game_id, game_id, name, have_owned, username) %>%
  pivot_wider(names_from = "username",
              values_from = "have_owned",
              values_fn = max) %>%
  mutate_if(is.numeric, replace_na, 0)


collection_pivot %>%
  mutate(num_own = rowSums(across(.cols = Quinns:Gyges))) %>%
  arrange(desc(num_own)) %>%
  select(yearpublished, game_id, name, num_own, everything()) %>%
  mutate_at(vars("Quinns", "TomVasel", "ZeeGarcia", "rahdo", "Watch_It_Played", "NoPunIncluded", "Gyges"),
            ~ case_when(. == 1 ~ "✓",
                      TRUE ~ "")) %>%
  mutate(game_id = as.character(game_id),
         yearpublished = as.character(yearpublished)) %>%
  mutate(name = abbreviate(name, minlength=40)) %>%
  rename(Published = yearpublished,
         Game_ID = game_id,
         Name = name,
         Total  = num_own) %>%
  filter(Total > 1) %>%
  head(50) %>%
  flextable() %>%
  flextable::autofit() %>%
  flextable::align(., j = c("Published", "Game_ID", "Name"), align = "left", part = "body") %>%
  flextable::align(., j = c("Total"), align = "center", part = "header") %>%
  flextable::align(., j = c("Total", "Quinns", "TomVasel", "ZeeGarcia", "rahdo", "Watch_It_Played", "NoPunIncluded", "Gyges"), align = "center", part = "body") %>%
  bg(., j = "Total",
     bg = col_num_func) %>%
    color(., j = c("Quinns", "TomVasel", "ZeeGarcia", "rahdo", "Watch_It_Played", "NoPunIncluded", "Gyges"),
     color = "blue3") %>%
    set_caption("Collection Overlap Between Prominent Reviewers")

  
```

Which collections overlap the most?

```{r upset plot, fig.height=8, fig.width=11}

collection_pivot %>%
  select(-yearpublished, -game_id, -name) %>%
  as.data.frame() %>%
  UpSetR::upset(.,
              nsets = 50,
              show.numbers = F,
                 text.scale = 3,
                 point.size = 4,
                  line.size=1.5,
              #    nintersects = 50,
              mb.ratio = c(.4, .6),
              mainbar.y.label = "# of Games Played \n by Combination of User",
              sets.x.label = "# of Games by User",
              order.by = "freq")

collection_pivot %>%
      mutate(num_own = rowSums(across(.cols = Quinns:Gyges))) %>%
  filter(num_own > 1) %>%
  select(-yearpublished, -game_id, -name) %>%
  as.data.frame() %>%
  UpSetR::upset(.,
              nsets = 50,
              show.numbers = F,
                 text.scale = 3,
                 point.size = 4,
                  line.size=1.5,
              #    nintersects = 50,
              mb.ratio = c(.4, .6),
              mainbar.y.label = "# of Games Owned \n by Combination of User",
              sets.x.label = "# of Games by User",
              order.by = "freq")

```

What about by rating?

```{r rating mean and variance, warning=F, message=F}

# mean
collection_info %>%
  filter(!is.na(yearpublished)) %>%
  filter(!is.na(name)) %>%
  filter(username != 'mrbananagrabber') %>%
  filter(!is.na(rating)) %>%
  select(yearpublished, game_id, game_id, name, username, rating) %>%
  pivot_wider(names_from = "username",
              values_from = "rating",
              values_fn = max) %>%
  mutate_if(is.numeric, round, 1) %>%
  melt(., id.vars = c("yearpublished", "game_id", "name")) %>%
  group_by(yearpublished, game_id, name) %>%
  na.omit() %>%
  mutate(num_owned = n_distinct(variable)) %>%
  filter(num_owned > 2) %>%
  mutate(mean = mean(value, na.rm= T),
         sd = sd(value, na.rm=T)) %>%
  pivot_wider(names_from = "variable",
              values_from = c("value")) %>%
  mutate_if(is.numeric, round, 1) %>%
  ungroup() %>%
  mutate(name = abbreviate(name, minlength=30)) %>%
  arrange(desc(mean)) %>%
  mutate(yearpublished = as.character(yearpublished),
         game_id = as.character(game_id)) %>%
  rename(Owned = num_owned,
         Mean = mean,
         Name = name,
         ID = game_id,
         SD = sd, 
         Published = yearpublished) %>%
  select(-Owned) %>%
  head(50) %>%
  flextable() %>%
  flextable::autofit() %>% 
  bg(., j = 'Mean',
     bg = col_func) %>%
  flextable::align(., j = c("Mean", "SD", "Quinns", "TomVasel", "ZeeGarcia", "rahdo", "Gyges"), align = "center", part = "body") %>%
    bg(., j = c("Quinns", "TomVasel", "ZeeGarcia", "rahdo", "Gyges"),
     bg = col_func) %>%
      set_caption("Highest Rated Games for Selected Reviewers")


# mean
collection_info %>%
  filter(!is.na(yearpublished)) %>%
  filter(!is.na(name)) %>%
  filter(username != 'mrbananagrabber') %>%
  filter(!is.na(rating)) %>%
  select(yearpublished, game_id, game_id, name, username, rating) %>%
  pivot_wider(names_from = "username",
              values_from = "rating",
              values_fn = max) %>%
  mutate_if(is.numeric, round, 1) %>%
  melt(., id.vars = c("yearpublished", "game_id", "name")) %>%
  group_by(yearpublished, game_id, name) %>%
  na.omit() %>%
  mutate(num_owned = n_distinct(variable)) %>%
  filter(num_owned > 2) %>%
  mutate(mean = mean(value, na.rm= T),
         sd = sd(value, na.rm=T)) %>%
  pivot_wider(names_from = "variable",
              values_from = c("value")) %>%
  mutate_if(is.numeric, round, 1) %>%
  ungroup() %>%
  mutate(name = abbreviate(name, minlength=30)) %>%
  arrange(desc(sd)) %>%
  mutate(yearpublished = as.character(yearpublished),
         game_id = as.character(game_id)) %>%
  rename(Owned = num_owned,
         Mean = mean,
         Name = name,
         ID = game_id,
         SD = sd, 
         Published = yearpublished) %>%
  select(-Owned) %>%
  head(50) %>%
  flextable() %>%
  flextable::autofit() %>% 
  bg(., j = 'Mean',
     bg = col_func) %>%
  flextable::align(., j = c("Mean", "SD", "Quinns", "TomVasel", "ZeeGarcia", "rahdo", "Gyges"), align = "center", part = "body") %>%
    bg(., j = c("Quinns", "TomVasel", "ZeeGarcia", "rahdo", "Gyges"),
     bg = col_func) %>%
      set_caption("Highest Variance Games for Selected Reviewers")

```

## Analysis

### Create Training Set

```{r whiteflag publishers}

game_publishers %>% 
        group_by(publisher_id, publisher) %>% 
        summarize(games = n_distinct(game_id)) %>% arrange(desc(games))

publisher_list = c(51,
                   4,
                   157,
                   34,
                   28,
                   10001,
                   39,
                   37,
                   20,
                   3,
                   538,
                   52,
                   8923,
                   17,
                   5,
                   3320,
                   597,
                   5400,
                   26,
                   47,
                   2726,
                   11652,
                   19,
                   13,
                   12024,
                   28072)

```


```{r pivot and join}

min_users = 200

# combine all
games_train<-active_games %>%
  select(timestamp, game_id, name, average, baverage, usersrated) %>%
  filter(usersrated > min_users) %>%
  left_join(., games_info %>% # join game info
              select(game_id, yearpublished, avgweight, minage, minplayers, maxplayers, playingtime),
            by = c("game_id")) %>%
  filter(yearpublished < 2020) %>% # use games prior to 2020 as our training set
  left_join(., game_categories %>% # join categories
              mutate(category = gsub("\\)", "", gsub("\\(", "", category))) %>%
              mutate(category = tolower(paste("cat", gsub("[[:space:]]", "_", gsub("\\s+", " ", gsub("[[:punct:]]","", category))), sep="_"))) %>%
              mutate(has_category = 1) %>%
              select(-category_id) %>%
              pivot_wider(names_from = c("category"),
                          values_from = c("has_category"),
                          id_cols = c("game_id"),
                          names_sep = "_",
                          values_fn = min,
                          values_fill = 0),
            by = c("game_id")) %>%
  left_join(., game_mechanics %>% # join mechanics
              mutate(mechanic = tolower(paste("mech", gsub("[[:space:]]", "_", gsub("\\s+", " ", gsub("[[:punct:]]","", mechanic))), sep="_"))) %>%
              mutate(has_mechanic = 1) %>%
              select(-mechanic_id) %>%
              pivot_wider(names_from = c("mechanic"),
                          values_from = c("has_mechanic"),
                          id_cols = c("game_id"),
                          names_sep = "_",
                          values_fn = min,
                          values_fill = 0),
            by = c("game_id")) %>%
      left_join(., game_designers %>% # join designers
              mutate(designer = gsub("\\)", "", gsub("\\(", "", designer))) %>%
              mutate(designer = tolower(paste("des", gsub("[[:space:]]", "_", gsub("\\s+", " ", gsub("[[:punct:]]","", designer))), sep="_"))) %>%
              mutate(has_designer = 1) %>%
              select(-designer_id) %>%
              pivot_wider(names_from = c("designer"),
                          values_from = c("has_designer"),
                          id_cols = c("game_id"),
                          names_sep = "_",
                          values_fn = min,
                          values_fill = 0),
            by = c("game_id")) %>%
        left_join(., game_publishers %>% # join publishers
                          filter(publisher_id %in% publisher_list) %>%
              mutate(publisher = gsub("\\)", "", gsub("\\(", "", publisher))) %>%
              mutate(publisher = tolower(paste("pub", gsub("[[:space:]]", "_", gsub("\\s+", " ", gsub("[[:punct:]]","", publisher))), sep="_"))) %>%
              mutate(has_publisher = 1) %>%
              select(-publisher_id) %>%
              pivot_wider(names_from = c("publisher"),
                          values_from = c("has_publisher"),
                          id_cols = c("game_id"),
                          names_sep = "_",
                          values_fn = min,
                          values_fill = 0),
              by = c("game_id")) %>%
      left_join(., 
                game_collections %>%
                mutate(username = case_when(username == 'Watch%20It%20Played' ~ 'Watch_It_Played',
                                            TRUE ~ username)) %>%
                mutate(own = case_when(username == 'TomVasel' & rating >= 8 ~ 1,
                         TRUE ~ own)) %>%
                mutate(have_played = case_when(own == 1 | prevowned == 1 | !(is.na(rating)) ~ 1,
                                               TRUE ~ 0)) %>%
                mutate(have_owned = case_when(own == 1 | prevowned == 1 | (username == 'Quinns' & !is.na(rating)) ~ 1,
                                              TRUE ~ 0)) %>%
                select(game_id, own, have_owned, have_played, rating, username) %>%
                pivot_wider(names_from = c("username"),
                            values_from = c("own", "have_owned", "have_played", "rating"),
                            values_fn = max,
                            id_cols = game_id) %>%
                mutate_at(vars(starts_with("have_owned_")),
                         ~ replace_na(., 0)) %>%
                  mutate_at(vars(starts_with("own_")),
                         ~ replace_na(., 0)),
                mutate_at(vars(starts_with("have_played_")),
                         ~ replace_na(., 0)),
                by = c("game_id"))
  
```


### PCA

We'll create a recipe for an initial PCA first. Then we'll create a recipe for our baseline model, which only uses observable game info such as playing time, player counts, complexity (more on this later), and categories + mechanics.

A couple of things to note here. We're going to filter to games published since 1950, as well as filter to games with a set number of user ratings.

```{r recipe for pca}

recipe_pca<- recipe(~ .,
                    x = games_train) %>%
  update_role(all_numeric(),
              new_role = "predictor") %>%
          update_role(timestamp,
                usersrated,
                game_id,
                name,
                average,
                baverage,
                new_role = "id") %>%
  step_filter(!is.na(yearpublished)) %>%
  step_filter(
              cat_collectible_components !=1 &
              cat_expansion_for_basegame != 1) %>% # remove specific categories that count expansions
         # step_filter(yearpublished > 1950) %>%
         # step_mutate(published_prior_1900 = case_when(yearpublished<1900 ~ 1,
         #                                                     TRUE ~ 0)) %>%
         #  step_mutate(yearpublished = case_when(yearpublished <= 1900 ~ 1900,
         #                                         TRUE ~ as.numeric(yearpublished))) %>% # truncate yearpublished
         # step_mutate(years_since_published = as.numeric(year(Sys.Date()))-yearpublished) %>%
  step_impute_median(avgweight,
                            minplayers,
                            maxplayers,
                            playingtime,
                            minage) %>% # medianimpute numeric predictors
  step_mutate(minplayers = case_when(minplayers < 1 ~ 1,
                                             minplayers > 10 ~ 10,
                                             TRUE ~ minplayers),
              maxplayers = case_when(maxplayers < 1 ~ minplayers,
                                             maxplayers > 20 ~ 20,
                                             TRUE ~ maxplayers)) %>% # truncate player range
  step_mutate(time_per_player = playingtime/ maxplayers) %>% # make time per player variable
  step_mutate_at(starts_with("cat_"),
                   fn = ~ replace_na(., 0)) %>%
  step_mutate_at(starts_with("mech_"),
                   fn = ~ replace_na(., 0)) %>%
  step_mutate_at(starts_with("des_"),
                   fn = ~ replace_na(., 0)) %>%
  step_mutate_at(starts_with("pub_"),
                   fn = ~ replace_na(., 0)) %>%
   step_mutate_at(starts_with("own_"),
                   fn = ~ replace_na(., 0)) %>%
  step_mutate_at(starts_with("have_owned_"),
                   fn = ~ replace_na(., 0)) %>%
    step_mutate_at(starts_with("have_played_"),
                   fn = ~ replace_na(., 0)) %>%
  step_mutate(number_mechanics = rowSums(across(starts_with("mech_"))),
                      number_categories = rowSums(across(starts_with("cat_"))),
                      number_designers = rowSums(across(starts_with("des_")))) %>%
  update_role(starts_with("have_owned"),
              starts_with("have_played"),
              starts_with("own_"),
              starts_with("rating_"),
              new_role = "id") %>%
  step_rm(starts_with("des_"),
          starts_with("pub_")) %>%
  step_log(playingtime,
           time_per_player,
           offset = 1) %>%
  step_zv(all_predictors()) %>%
  step_nzv(all_predictors(),
           freq_cut = 150/1) %>%
  step_normalize(all_numeric_predictors()) %>%
  check_missing(all_numeric_predictors()) %>%
  step_pca(all_numeric_predictors(),
           num_comp = 10) 

```

Now apply the PCA

```{r apply pca}

pca_estimates = prep(recipe_pca,
                     training = games_train)

pca_data <- bake(pca_estimates, 
                 games_train)

```

Plot the first few principal components.

```{r plot plca, fig.height=8}

set.seed(1999)
pca_data %>%
  ggplot(., aes(x=PC01,
                label = name,
                y=PC02))+
  geom_jitter(alpha=0.5,
              width=0.4,
              height = 0.1)+
  geom_text(check_overlap = T,
            size = 2,
            position=position_jitter(width=0.4,height=0.2))+
  theme_phil()

# set.seed(1999)
# pca_data %>%
#   ggplot(., aes(x=PC01,
#                 label = name,
#                 y=PC03))+
#   geom_jitter(alpha=0.5,
#               width=0.4,
#               height = 0.1)+
#   geom_text(check_overlap = T,
#             size = 2,
#             position=position_jitter(width=0.4,height=0.2))+
#   theme_phil()

```

We can use this to get a general sense of the landscape of games.

```{r publishers in pca 1, message=F, fig.height=8}

ggplot(pca_data, aes(x=PC01,
              #  color = Fantasy_Flight,
               label = name,
                y=PC02))+
  geom_point(col = 'grey60',
             alpha=0.25)+
  # geom_jitter(aes(color = Fantasy_Flight),
  #             width=0.4,
  #             height = 0.1)+
  geom_text(check_overlap = T,
            size = 2,
   position=position_jitter(width=0.4,height=0.2))+
  theme_phil()+
  geom_vline(xintercept = 0)+
  geom_hline(yintercept = 0)+
  my_caption
  

p =   ggplot(pca_data, aes(x=PC01,
              #  color = Fantasy_Flight,
            #   label = name,
                y=PC02))+
  geom_point(col = 'grey60',
             alpha=0.25)+
  # geom_jitter(aes(color = Fantasy_Flight),
  #             width=0.4,
  #             height = 0.1)+
  # geom_text(check_overlap = T,
  #           size = 2)+
          #  position=position_jitter(width=0.4,height=0.2))+
  theme_phil()+
  geom_vline(xintercept = 0)+
  geom_hline(yintercept = 0) +
  annotate(geom="label",
                x=10, y=4,
           label = "Simulation & Wargames")+
  annotate(geom="label",
                x=-5, y=-3,
           label = "Party Games")+
  annotate(geom="label",
                x=-5, y=3,
           label = "Abstracts")+
  annotate(geom="label",
                x=0, y=1,
           label = "Euros")+
  annotate(geom="label",
                x=6, y=-6,
           label = "Thematic")+
  my_caption

p

```

#### Publishers

We can highlight publishers in this to see where they generally fall. Fantasy Flight tends to be in the more thematic area.

```{r publishers in pca 2, fig.height=8}

## Fantasy Flight
set.seed(1999)
p + 
  geom_point(data = 
               pca_data %>%
  left_join(., games_train %>%
              select(game_id, starts_with("pub")),
            by = "game_id") %>%
  mutate(Fantasy_Flight = case_when(pub_fantasy_flight_games == 1 ~ 'Published',
                                    TRUE ~ 'no')) %>%
    filter(Fantasy_Flight == 'Published'),
  aes(x=PC01,
      y=PC02,
      color = Fantasy_Flight))+
  geom_text(data = 
              pca_data %>%
              left_join(., games_train %>%select(game_id, starts_with("pub")),
                        by = "game_id") %>%
              mutate(Fantasy_Flight = case_when(pub_fantasy_flight_games == 1 ~ 'Published',
                                                TRUE ~ 'no')) %>%
              filter(Fantasy_Flight == 'Published'),
  aes(label = name,
      color = Fantasy_Flight),
  check_overlap = T,
             size = 2,
             position=position_jitter(width=0.4,height=0.2))+
  theme(legend.title = element_text())+
  scale_color_manual(values = c("navy"))

```

As opposed to Pegasus Spiele, which is more in the Euro and Abstract area.

```{r publishers in pca pegasus, fig.height=8}

## Pegasus Spiele
set.seed(1999)
p+ geom_point(data = 
  pca_data %>%
  left_join(., games_train %>%
              select(game_id, starts_with("pub")),
            by = "game_id") %>%
  mutate(Pegasus_Spiele = case_when(pub_pegasus_spiele == 1 ~ 'Published',
                                    TRUE ~ 'no')) %>%
    filter(Pegasus_Spiele == 'Published'),
  aes(x=PC01,
      y=PC02,
      color = Pegasus_Spiele))+
  geom_text(data = 
              pca_data %>%
  left_join(., games_train %>%
              select(game_id, starts_with("pub")),
            by = "game_id") %>%
              mutate(Pegasus_Spiele = case_when(pub_pegasus_spiele== 1 ~ 'Published',
                                                TRUE ~ 'no')) %>%
              filter(Pegasus_Spiele == 'Published'),
  aes(label = name,
      color = Pegasus_Spiele),
  check_overlap = T,
             size = 2,
             position=position_jitter(width=0.4,height=0.2))+
  theme(legend.title = element_text())+
  scale_color_manual(values = c("darkred"))
```


Pretty similar for Rio Grande.

```{r publishers in pca rio grande, fig.height=8}

# Rio Grande
set.seed(1999)
p + 
  geom_point(data = 
  pca_data %>%
  left_join(., games_train %>%
              select(game_id, starts_with("pub")),
            by = "game_id") %>%
  mutate(Rio_Grande_Games = case_when(pub_rio_grande_games == 1 ~ 'Published',
                                    TRUE ~ 'no')) %>%
    filter(Rio_Grande_Games == 'Published'),
  aes(x=PC01,
      y=PC02,
      color = Rio_Grande_Games))+
  geom_text(data = 
              pca_data %>%
              left_join(., games_train %>%select(game_id, starts_with("pub"))) %>%
              mutate(Rio_Grande_Games = case_when(pub_rio_grande_games== 1 ~ 'Published',
                                                TRUE ~ 'no')) %>%
              filter(Rio_Grande_Games == 'Published'),
  aes(label = name,
      color = Rio_Grande_Games),
  check_overlap = T,
             size = 2,
             position=position_jitter(width=0.4,height=0.2))+
  theme(legend.title = element_text())+
  scale_color_manual(values = c("blue"))

```

..and Zman

```{r publishers in Zman, fig.height=8}

# ZMan
set.seed(1999)
p + 
  geom_point(data = 
  pca_data %>%
 left_join(., games_train %>%
              select(game_id, starts_with("pub")),
            by = "game_id") %>%
  mutate(ZMan_Games = case_when(pub_zman_games == 1 ~ 'Published',
                                    TRUE ~ 'no')) %>%
    filter(ZMan_Games == 'Published'),
  aes(x=PC01,
      y=PC02,
      color = ZMan_Games))+
  geom_text(data = 
              pca_data %>%
 left_join(., games_train %>%
              select(game_id, starts_with("pub")),
            by = "game_id") %>%
              mutate(ZMan_Games = case_when(pub_zman_games== 1 ~ 'Published',
                                                TRUE ~ 'no')) %>%
              filter(ZMan_Games == 'Published'),
  aes(label = name,
      color = ZMan_Games),
  check_overlap = T,
             size = 2,
             position=position_jitter(width=0.4,height=0.2))+
  theme(legend.title = element_text())+
  scale_color_manual(values = c("black"))

```

GMT is perhaps the most distinctive.

```{r publishers in GMT, fig.height=8}

# GMT
set.seed(1999)
p + 
  geom_point(data = 
  pca_data %>%
 left_join(., games_train %>%
              select(game_id, starts_with("pub")),
            by = "game_id") %>%
  mutate(GMT_Games = case_when(pub_gmt_games == 1 ~ 'Published',
                                    TRUE ~ 'no')) %>%
    filter(GMT_Games == 'Published'),
  aes(x=PC01,
      y=PC02,
      color = GMT_Games))+
  geom_text(data = 
              pca_data %>%
 left_join(., games_train %>%
              select(game_id, starts_with("pub")),
            by = "game_id") %>%
              mutate(GMT_Games = case_when(pub_gmt_games== 1 ~ 'Published',
                                                TRUE ~ 'no')) %>%
              filter(GMT_Games == 'Published'),
  aes(label = name,
      color = GMT_Games),
  check_overlap = T,
             size = 2,
             position=position_jitter(width=0.4,height=0.2))+
  theme(legend.title = element_text())+
  scale_color_manual(values = c("red2"))

```

### Individuals

We can do the same thing for individuals, plotting the games they own. Quinns' collection is pretty much all over, as he has a pretty diverse collection.

```{r place reviewers quinns, message=F, fig.height=8, eval = F}

# Quinns
set.seed(1999)
p + 
  geom_point(data = 
               pca_data %>%
               mutate(Quinns = case_when(have_owned_Quinns == 1 ~ 'In Collection',
                             TRUE ~ 'no')) %>%
               filter(Quinns == 'In Collection'),
  aes(x=PC01,
      y=PC02,
      color = Quinns))+
  geom_text(data = 
               pca_data %>%
               mutate(Quinns = case_when(have_owned_Quinns == 1 ~ 'In Collection',
                             TRUE ~ 'no')) %>%
               filter(Quinns == 'In Collection'),
  aes(label = name,
      color = Quinns),
  check_overlap = T,
  size = 2,
  position=position_jitter(width=0.4,height=0.2))+
  theme(legend.title = element_text())+
  scale_color_manual(values = c("navy"))

```

Rahdo

```{r place reviewers rahdo, message=F, fig.height=8}

# rahdo
set.seed(1999)
p + 
  geom_point(data = 
               pca_data %>%
               mutate(rahdo = case_when(have_owned_rahdo == 1 ~ 'In Collection',
                             TRUE ~ 'no')) %>%
               filter(rahdo == 'In Collection'),
  aes(x=PC01,
      y=PC02,
      color = rahdo))+
  geom_text(data = 
               pca_data %>%
               mutate(rahdo = case_when(have_owned_rahdo == 1 ~ 'In Collection',
                             TRUE ~ 'no')) %>%
               filter(rahdo == 'In Collection'),
  aes(label = name,
      color = rahdo),
  check_overlap = T,
  size = 2,
  position=position_jitter(width=0.4,height=0.2))+
  theme(legend.title = element_text())+
  scale_color_manual(values = c("navy"))

```

Mark Bigney

```{r place reviewers mark bigney, message=F, fig.height=8}

# Gyges
set.seed(1999)
p + 
  geom_point(data = 
               pca_data %>%
               mutate(Gyges = case_when(have_owned_Gyges == 1 ~ 'In Collection',
                             TRUE ~ 'no')) %>%
               filter(Gyges == 'In Collection'),
  aes(x=PC01,
      y=PC02,
      color = Gyges))+
  geom_text(data = 
               pca_data %>%
               mutate(Gyges = case_when(have_owned_Gyges == 1 ~ 'In Collection',
                             TRUE ~ 'no')) %>%
               filter(Gyges == 'In Collection'),
  aes(label = name,
      color = Gyges),
  check_overlap = T,
  size = 2,
  position=position_jitter(width=0.4,height=0.2))+
  theme(legend.title = element_text())+
  scale_color_manual(values = c("navy"))

```

ZeeGaria

```{r place reviewers watch it played, message=F, fig.height=8}

# ZeeGarcia
set.seed(1999)
p + 
  geom_point(data = 
               pca_data %>%
               mutate(ZeeGarcia = case_when(have_owned_ZeeGarcia == 1 ~ 'In Collection',
                             TRUE ~ 'no')) %>%
               filter(ZeeGarcia == 'In Collection'),
  aes(x=PC01,
      y=PC02,
      color = ZeeGarcia))+
  geom_text(data = 
               pca_data %>%
               mutate(ZeeGarcia = case_when(have_owned_ZeeGarcia == 1 ~ 'In Collection',
                             TRUE ~ 'no')) %>%
               filter(ZeeGarcia == 'In Collection'),
  aes(label = name,
      color = ZeeGarcia),
  check_overlap = T,
  size = 2,
  position=position_jitter(width=0.4,height=0.2))+
  theme(legend.title = element_text())+
  scale_color_manual(values = c("navy"))


```

## Training Models

We'll now create the recipe for predictive modeling.

```{r create recipes}

recipe_model<- recipe(~ .,
                    x = games_train) %>%
  update_role(all_numeric(),
              new_role = "predictor") %>%
  update_role(timestamp,
                usersrated,
                game_id,
                name,
                average,
                baverage,
                new_role = "id") %>%
  update_role(starts_with("have_owned"),
              starts_with("have_played"),
              starts_with("own_"),
              starts_with("rating_"),
              new_role = "id") %>%
  step_filter(!is.na(yearpublished)) %>%
  step_filter(
              cat_collectible_components !=1 &
              cat_expansion_for_basegame != 1) %>% # remove specific categories that count expansions
  step_filter(yearpublished > 1950) %>%
  step_mutate(published_prior_1900 = case_when(yearpublished<1900 ~ 1,
                                               TRUE ~ 0)) %>%
  step_mutate(yearpublished = case_when(yearpublished <= 1900 ~ 1900,
                                               TRUE ~ as.numeric(yearpublished))) %>% # truncate yearpublished
 # step_mutate(years_since_published = as.numeric(year(Sys.Date()))-yearpublished) %>%
  step_impute_median(avgweight,
                            minplayers,
                            maxplayers,
                            playingtime,
                            minage) %>% # medianimpute numeric predictors
  step_mutate(minplayers = case_when(minplayers < 1 ~ 1,
                                             minplayers > 10 ~ 10,
                                             TRUE ~ minplayers),
              maxplayers = case_when(maxplayers < 1 ~ minplayers,
                                             maxplayers > 20 ~ 20,
                                             TRUE ~ maxplayers)) %>% # truncate player range
  step_mutate(time_per_player = playingtime/ maxplayers) %>% # make time per player variable
   step_mutate_at(starts_with("cat_"),
                   fn = ~ replace_na(., 0)) %>%
  step_mutate_at(starts_with("mech_"),
                   fn = ~ replace_na(., 0)) %>%
  step_mutate_at(starts_with("des_"),
                   fn = ~ replace_na(., 0)) %>%
  step_mutate_at(starts_with("pub_"),
                   fn = ~ replace_na(., 0)) %>%
   step_mutate_at(starts_with("own_"),
                   fn = ~ replace_na(., 0)) %>%
  step_mutate_at(starts_with("have_owned_"),
                   fn = ~ replace_na(., 0)) %>%
    step_mutate_at(starts_with("have_played_"),
                   fn = ~ replace_na(., 0)) %>%
  step_mutate(number_mechanics = rowSums(across(starts_with("mech_"))),
                      number_categories = rowSums(across(starts_with("cat_"))),
                      number_designers = rowSums(across(starts_with("des_")))) %>%
  step_log(playingtime,
           time_per_player,
           offset = 1) %>%
  step_zv(all_predictors()) %>%
  step_nzv(all_predictors(),
           freq_cut = 150/1)

# normalize
recipe_norm_model<-recipe_model %>%
  step_poly(number_mechanics, degree = 2) %>%
  step_normalize(all_predictors())

# summary of recipe
summary(recipe_model)

```

We will apply this formula to each outcome we care about. First, we'll be setting up our data to be nested at the username and outcome level.

```{r melt, warning = F}

# baked without normalization
baked_train= recipe_model %>%
  prep(games_train, strings_as_factor = F) %>%
  bake(new_data = NULL)

# baked with normalization
baked_train_norm = recipe_norm_model %>%
  prep(games_train, strings_as_factor = F) %>%
  bake(new_data = NULL)

# get all vars
vars=names(baked_train %>%
             select(-starts_with("rating_"),
                    -starts_with("own_"),
                    -starts_with("have_played"),
                    -starts_with("have_owned")))

# melt
melted_baked_train <- baked_train %>%
  melt(., id.vars = vars) %>%
  rename(outcome = value) %>%
  mutate(outcome_type = case_when(grepl("have_owned_", variable) ~ 'have_owned',
                                  grepl("own_", variable) ~ "own",
                                  grepl("have_played", variable) ~ "have_played",
                                  grepl("rating_", variable) ~ 'rating')) %>%
  mutate(outcome = case_when((outcome_type == 'own' | outcome_type == 'have_owned') & is.na(outcome) ~ 0,
                             TRUE ~ outcome)) %>%
  filter(!is.na(outcome)) %>%
  mutate(username = gsub("have_played_","", gsub("own_", "", gsub("rating_", "", gsub("have_owned_", "", variable))))) %>%
  select(username, outcome_type, outcome, variable, everything()) %>%
  nest(-username, -outcome_type, -variable)

```


### Model Control

```{r establish models in tidymodels}

library(tidymodels)
library(workflows)
library(rsample)

# simple linear regression
lm_mod <- 
  linear_reg() %>% 
  set_engine("lm")

# simple logistic regression
glm_mod <- 
  logistic_reg() %>% 
  set_engine("glm")

# stan linear regression
set.seed(123)
prior_dist <- rstanarm::student_t(df = 1)
stan_reg_mod <-   
  linear_reg() %>% 
  set_engine("stan", 
             prior_intercept = prior_dist, 
             prior = prior_dist,
             iter = 4000)

# stan linear regression
set.seed(123)
stan_class_mod <-   
  logistic_reg() %>% 
  set_engine("stan", 
             prior_intercept = prior_dist, 
             prior = prior_dist,
             iter = 4000)

# penalized linear regression
glmnet_reg_mod<- 
  linear_reg(penalty = tune::tune(),
             mixture = 0.5) %>%
  set_engine("glmnet")

# penalized logistic regression
glmnet_class_mod<- 
  logistic_reg(penalty = tune::tune(),
             mixture = 0.5) %>%
  set_engine("glmnet")

# specify grid for tuning
glmnet_grid <- tibble(penalty = 10^seq(-4, -0.5, 
                                       length.out = 30))


#XGBoost model specification
#reg
xgbTree_reg_mod <-
  parsnip::boost_tree(
    mode = "regression",
    trees = 1000,
    sample_size = tune::tune(),
    min_n = tune::tune(),
    tree_depth = tune::tune()) %>%
  set_engine("xgboost",
               objective = "reg:squarederror")

# # xgbTree model specifications without tuning
# xgbTree_reg_mod <-
#   parsnip::boost_tree(
#     mode = "regression",
#     trees = 500) %>%
#   set_engine("xgboost",
#                objective = "reg:squarederror")
# 
# xgbTree_class_mod <-
#   parsnip::boost_tree(
#     mode = "classification",
#     trees = 500) %>%
#   set_engine("xgboost")

# ranger model spec without tuning
ranger_reg_mod <- 
  parsnip::rand_forest(
    mode = "regression",
    trees = 500) %>%
  set_engine("ranger",
               objective = "reg:squarederror")

ranger_class_mod <- 
  parsnip::rand_forest(
    mode = "classification",
    trees = 500) %>%
  set_engine("ranger")


# class
xgbTree_class_mod <-
  parsnip::boost_tree(
    mode = "classification",
    trees = 1000,
    sample_size = tune::tune(),
    min_n = tune::tune(),
    tree_depth = tune::tune()) %>%
  set_engine("xgboost")



# grid
xgbTree_grid <- 
  expand.grid(
    sample_size = c(0.5, 0.75, 0.95),
    min_n = c(5, 15, 25),
    tree_depth = 3
  )

# specify regression metrics
reg_metrics<-metric_set(yardstick::rmse,
                        yardstick::rsq,
                        yardstick::mae,
                        yardstick::mape)

# specify regression metrics
class_metrics<-metric_set(yardstick::roc_auc,
                          yardstick::mn_log_loss)

```

We'll then create workflows out of each of these.

```{r create functions for tidymodels workflows}

# function for standard recipe
recipe_function = function(df, setting) {
  
    # change to factor if classification
  if (setting == 'classification') {df$outcome = as.factor(df$outcome)}
  else if (setting == 'regression') {df$outcome = df$outcome} 
  else {'select classification or regression'}
  
  norm_recipe = recipe_train <-
    recipe(outcome ~ ., data = df) %>%
    update_role(timestamp,
                usersrated,
                game_id,
                name,
                average,
                baverage,
                new_role = "id") %>%
    step_zv(all_predictors()) %>%
    step_corr(all_predictors(),
              threshold = 0.95) 
}

# function for normalized recipe
norm_recipe_function = function(df, setting) {
  
    # change to factor if classification
  if (setting == 'classification') {df$outcome = as.factor(df$outcome)}
  else if (setting == 'regression') {df$outcome = df$outcome} 
  else {'select classification or regression'}
  
  norm_recipe = recipe_train <-
    recipe(outcome ~ ., data = df) %>%
    update_role(timestamp,
                usersrated,
                game_id,
                name,
                average,
                baverage,
                new_role = "id") %>%
    step_zv(all_predictors()) %>%
    step_corr(all_predictors(),
              threshold = 0.95) %>%
    step_normalize(all_predictors())
  
}
  
# function for fitting workflow using a selected model and recipe
fit_workflow_function <- function(df, input_model, input_recipe, metrics) {
  
      # change to factor if classification
  if (metrics == 'classification') {df$outcome = as.factor(df$outcome)}
  else if (metrics == 'regression') {df$outcome = df$outcome} 
  else {'select classification or regression'}

  # fit model
  fit_wf <-
    workflow() %>%
    add_model(input_model) %>%
    add_recipe(input_recipe) %>%
    fit(df)

  
}

# function for tuning a workflow over folds
tune_workflow_function <- function(df, input_model, input_recipe, input_grid, metrics) {
  
# change to factor if classification
  if (metrics == 'classification') {df$outcome = as.factor(df$outcome)}
  else if (metrics == 'regression') {df$outcome = df$outcome} 
  else {'select classification or regression'}
  
    # create folds
  set.seed(1999)
  train_folds = vfold_cv(df,
            strata = outcome,
            v = 5,
            repeats = 1)

  # if regression then
  if (metrics == "regression") {
  fit_wf <-
    workflow() %>%
    add_model(input_model) %>%
    add_recipe(input_recipe) %>%
    tune_grid(train_folds,
            grid = input_grid,
            control = control_grid(save_pred = TRUE),
            metrics = reg_metrics)
  } else if (metrics == "classification") {
    fit_wf <-
    workflow() %>%
    add_model(input_model) %>%
    add_recipe(input_recipe) %>%
    tune_grid(train_folds,
            grid = input_grid,
            control = control_grid(save_pred = TRUE),
            metrics = class_metrics)
  } else {"select regression or classification"}
  
}


## for finalizing workflow
# function to finalize workflow using tune results
finalize_workflow_function<- function(df, input_model, input_recipe, tune_results, metrics) {
  
  # change to factor if classification
  if (metrics == 'classification') {df$outcome = as.factor(df$outcome)}
  else if (metrics == 'regression') {df$outcome = df$outcome} 
  else {'select classification or regression'}

  #fit workflow on train data
  fit_wf <-
    workflow() %>%
    add_model(input_model) %>%
    add_recipe(input_recipe)
  
  # finalize workflow
  final_wf <-
    fit_wf %>%
    finalize_workflow(tune_results) %>%
    fit(df)
  
}
   
```

### Fitting Models

We can now fit models for each outcome we are interested in.

```{r fit and tune ratings models with workflows, message=F, warning=F}

cores = parallel::detectCores()-1
doParallel::registerDoParallel(cores)

set.seed(1999)
# ratings
ratings_models = melted_baked_train %>%
  filter(outcome_type == 'rating') %>%
  # mutate(stan_lm = map(data,
  #                           ~  fit_workflow_function(df = .x,
  #                                                    input_model = stan_reg_mod,
  #                                                    input_recipe = norm_recipe_function(.x, setting = 'regression'),
  #                                                    metrics = "regression"))) %>%
  mutate(glmnet_tune = map(data,
                          ~ tune_workflow_function(df = .x,
                                                     input_model = glmnet_reg_mod,
                                                   input_grid = glmnet_grid,
                                                     input_recipe = norm_recipe_function(.x, setting = 'regression'),
                                                     metrics = 'regression'))) 
  # mutate(xgbTree_tune = map(data, ~ tune_workflow_function(df = .x,
  #                                                    input_model = xgbTree_reg_mod,
  #                                                    input_grid = xgbTree_grid,
  #                                                    input_recipe = norm_recipe_function(.x, setting = 'regression'),
  #                                                    metrics = "regression"))) %>%
  # mutate(ranger = map(data, ~ fit_workflow_function(df = .x,
  #                                                    input_model = ranger_reg_mod,
  #                                                    input_recipe = norm_recipe_function(.x, setting = 'regression'),
  #                                                    metrics = "regression")))

set.seed(1999)
# have owned
have_owned_models = melted_baked_train %>%
  filter(username != 'NoPunIncluded') %>%
  filter(outcome_type == 'have_owned') %>%
  # mutate(stan_lm = map(data,
  #                           ~  fit_workflow_function(df = .x,
  #                                                    input_model = stan_class_mod,
  #                                                    input_recipe = norm_recipe_function(.x, setting = 'classification'),
  #                                                    metrics = 'classification'))) %>%
  mutate(glmnet_tune = map(data,
                          ~ tune_workflow_function(df = .x,
                                                     input_model = glmnet_class_mod,
                                                   input_grid = glmnet_grid,
                                                     input_recipe = norm_recipe_function(.x, setting = 'classification'),
                                                     metrics = 'classification'))) 

set.seed(1999)
# have played
have_played_models = melted_baked_train %>%
  filter(username != 'NoPunIncluded') %>%
  filter(outcome_type == 'have_played') %>%
  # mutate(stan_lm = map(data,
  #                           ~  fit_workflow_function(df = .x,
  #                                                    input_model = stan_class_mod,
  #                                                    input_recipe = norm_recipe_function(.x, setting = 'classification'),
  #                                                    metrics = 'classification'))) %>%
  mutate(glmnet_tune = map(data,
                          ~ tune_workflow_function(df = .x,
                                                     input_model = glmnet_class_mod,
                                                   input_grid = glmnet_grid,
                                                     input_recipe = norm_recipe_function(.x, setting = 'classification'),
                                                     metrics = 'classification'))) 
  # mutate(xgbTree_tune = map(data,
  #                         ~ tune_workflow_function(df = .x,
  #                                                    input_model = xgbTree_class_mod,
  #                                                  input_grid = xgbTree_grid,
  #                                                    input_recipe = norm_recipe_function(.x, setting = 'classification'),
  #                                                    metrics = 'classification'))) %>%
  # mutate(ranger = map(data,
  #                         ~ fit_workflow_function(df = .x,
  #                                                    input_model = ranger_class_mod,
  #                                                    input_recipe = norm_recipe_function(.x, setting = 'classification'),
  #                                                    metrics = 'classification'))) 
set.seed(1999)
# have owned
own_models = melted_baked_train %>%
  filter(outcome_type == 'own') %>%
  filter(username != 'NoPunIncluded') %>%
  # mutate(stan_lm = map(data,
  #                           ~  fit_workflow_function(df = .x,
  #                                                    input_model = stan_class_mod,
  #                                                    input_recipe = norm_recipe_function(.x, setting = 'classification'),
  #                                                    metrics = 'classification'))) %>%
  mutate(glmnet_tune = map(data,
                          ~ tune_workflow_function(df = .x,
                                                     input_model = glmnet_class_mod,
                                                   input_grid = glmnet_grid,
                                                     input_recipe = norm_recipe_function(.x, setting = 'classification'),
                                                     metrics = 'classification'))) 
  # mutate(xgbTree_tune = map(data,
  #                         ~ tune_workflow_function(df = .x,
  #                                                    input_model = xgbTree_class_mod,
  #                                                  input_grid = xgbTree_grid,
  #                                                    input_recipe = norm_recipe_function(.x, setting = 'classification'),
  #                                                    metrics = 'classification'))) %>%
  # mutate(ranger = map(data,
  #                         ~ fit_workflow_function(df = .x,
  #                                                    input_model = ranger_class_mod,
  #                                                    input_recipe = norm_recipe_function(.x, setting = 'classification'),
  #                                                    metrics = 'classification'))) 


```

For the tuning workflows, refit the models with the best parameters

```{r fit with best paramaters, message=F, warning=F}

# ratings
ratings_models <- ratings_models %>%
  mutate(glmnet_best = map(glmnet_tune, ~ .x %>% show_best(n=1))) %>%
  mutate(glmnet_results = map2(.x = glmnet_tune,
                               .y = glmnet_best,
                               ~ .x %>% collect_predictions(parameters = .y))) %>%
  mutate(glmnet_fit = map2(.x=data,
                                   .y = glmnet_best,
                                   ~ finalize_workflow_function(df = .x,
                                                        input_model = glmnet_reg_mod,
                                                        tune_results = .y,
                                                        input_recipe = norm_recipe_function(.x, setting = 'regression'),
                                                        metrics = "regression"))) 
  # mutate(xgbTree_best = map(xgbTree_tune, ~ .x %>% show_best(n=1))) %>%
  # mutate(xgbTree_results = map2(.x = xgbTree_tune,
  #                              .y = xgbTree_best,
  #                              ~ .x %>% collect_predictions(parameters = .y))) %>%
  # mutate(xgbTree_fit = map2(.x=data,
  #                                  .y = xgbTree_best,
  #                                  ~ finalize_workflow_function(df = .x,
  #                                                       input_model = xgbTree_reg_mod,
  #                                                       tune_results = .y,
  #                                                       input_recipe = norm_recipe_function(.x, setting = 'regression'),
  #                                                       metrics = "regression")))

# have played
have_owned_models <- have_owned_models %>%
  mutate(glmnet_best = map(glmnet_tune, ~ .x %>% show_best(n=1))) %>%
  mutate(glmnet_results = map2(.x = glmnet_tune,
                               .y = glmnet_best,
                               ~ .x %>% collect_predictions(parameters = .y))) %>%
  mutate(glmnet_fit = map2(.x=data,
                                   .y = glmnet_best,
                                   ~ finalize_workflow_function(df = .x,
                                                        input_model = glmnet_class_mod,
                                                        tune_results = .y,
                                                        input_recipe = norm_recipe_function(.x, setting = 'classification'),
                                                        metrics = "classification"))) 

# have owned
have_played_models <- have_played_models %>%
  mutate(glmnet_best = map(glmnet_tune, ~ .x %>% show_best(n=1))) %>%
  mutate(glmnet_results = map2(.x = glmnet_tune,
                               .y = glmnet_best,
                               ~ .x %>% collect_predictions(parameters = .y))) %>%
  mutate(glmnet_fit = map2(.x=data,
                                   .y = glmnet_best,
                                   ~ finalize_workflow_function(df = .x,
                                                        input_model = glmnet_class_mod,
                                                        tune_results = .y,
                                                        input_recipe = norm_recipe_function(.x, setting = 'classification'),
                                                        metrics = "classification"))) 
  # mutate(xgbTree_best = map(xgbTree_tune, ~ .x %>% show_best(n=1))) %>%
  # mutate(xgbTree_results = map2(.x = xgbTree_tune,
  #                              .y = xgbTree_best,
  #                              ~ .x %>% collect_predictions(parameters = .y))) %>%
  # mutate(xgbTree_fit = map2(.x=data,
  #                                  .y = xgbTree_best,
  #                                  ~ finalize_workflow_function(df = .x,
  #                                                       input_model = xgbTree_class_mod,
  #                                                       tune_results = .y,
  #                                                       input_recipe = norm_recipe_function(.x, setting = 'classification'),
  #                                                       metrics = "classification")))

# have owned
own_models <- own_models %>%
  mutate(glmnet_best = map(glmnet_tune, ~ .x %>% show_best(n=1))) %>%
  mutate(glmnet_results = map2(.x = glmnet_tune,
                               .y = glmnet_best,
                               ~ .x %>% collect_predictions(parameters = .y))) %>%
  mutate(glmnet_fit = map2(.x=data,
                                   .y = glmnet_best,
                                   ~ finalize_workflow_function(df = .x,
                                                        input_model = glmnet_class_mod,
                                                        tune_results = .y,
                                                        input_recipe = norm_recipe_function(.x, setting = 'classification'),
                                                        metrics = "classification"))) 
  # mutate(xgbTree_best = map(xgbTree_tune, ~ .x %>% show_best(n=1))) %>%
  # mutate(xgbTree_results = map2(.x = xgbTree_tune,
  #                              .y = xgbTree_best,
  #                              ~ .x %>% collect_predictions(parameters = .y))) %>%
  # mutate(xgbTree_fit = map2(.x=data,
  #                                  .y = xgbTree_best,
  #                                  ~ finalize_workflow_function(df = .x,
  #                                                       input_model = xgbTree_class_mod,
  #                                                       tune_results = .y,
  #                                                       input_recipe = norm_recipe_function(.x, setting = 'classification'),
  #                                                       metrics = "classification")))

```

We'll now combine these files into one model.

```{r fit models from tuning, warning=F}

# combine all models
all_models = bind_rows(ratings_models,
                       have_owned_models,
                       have_played_models,
                       own_models)

```

We'll save these so we can load them in later without having to re run everything...

```{r save the models}

# save
save(all_models, file = paste("reviewer_predictions_models/reviewer_", Sys.Date(), ".Rds", sep=""))

```

### Examining Coefficients

```{r get coefs from the models, warning =F, fig.width=11, fig.height=8}

training_coefs = all_models %>%
  filter(outcome_type == 'own' | outcome_type == 'have_played' | outcome_type == 'have_owned') %>%
  mutate(glmnet_coefs = map(glmnet_fit, ~ .x %>% extract_fit_parsnip() %>%
                              tidy())) %>%
  select(username, outcome_type, glmnet_coefs)

rename_func<-function(x) {
  
  x<-gsub("cat_memory", "cat_memory_game", x)
  x<-gsub("cat_spiessecret_agents", "cat_spies_secret_agents", x)
  x<-gsub("cat_","", x)
  x<-gsub("mech_","", x)
  x<-gsub("pub_","", x)
  x<-gsub("des_","", x)
  x<-gsub("avgweight", "Average Weight", x)
  x<-gsub("yearpublished", "Year Published", x)
  x<-gsub("minage", "Min Age", x)
  x<-gsub("playingtime", "Playing Time", x)
  x<-gsub("maxplayers", "Max Players", x)
  x<-gsub("minplayers", "Min Players", x)
  x<-gsub("_", " ", x)

  str_to_title(x)

}

# function for plotting
plot_coef_function <- function(coefs,
                               effect_size,
                               reviewer) {
  # for me
  coefs %>%
    unnest() %>%
    filter(term != '(Intercept)') %>%
    filter(username == paste(reviewer)) %>%
    mutate(term = rename_func(term)) %>%
    filter(abs(estimate) > effect_size ) %>%
    ggplot(., aes(x= reorder(term, estimate),
                  shape = outcome_type,
                  color = outcome_type,
                  y = estimate))+
    geom_point(alpha=0.6)+
    coord_flip()+
    facet_wrap(username ~.)+
    #scale_color_grey(start = 0.2, end = 0.6)+
    scale_color_colorblind()+
    theme_phil()+
    theme(axis.text.y = element_text(size=rel(0.75)))+
    geom_hline(yintercept = 0,
               linetype = 'dotted')+
    xlab("Feature")+
    ylab("Estimated Effect on Outcome")+
    labs(title = "What Predicts a Reviewer's Collection?",
         subtitle = str_wrap("Coefficients from penalized logistic regression models for a user's BGG Collection. 'Owned' model trained on whether user has game in collection on BGG. 'Have Owned' model trained on whether user owns or has previously owned game on BGG. Predictors centered and scaled. Models trained on all games published before 2020.", 90),
         caption= paste(paste("Data from boardgamegeek.com as of", max(as.Date(baked_train$timestamp))),
                        paste("Data and analysis at github.com/phenrickson/bgg"), sep="\n"))+
    theme(panel.grid.minor = element_blank(),
          panel.grid.major = element_blank())+
    my_caption

}

```


Let's look at the coefficient for myself to start. I'm not surprised by the effect for Fantasy Flight, as that's like half my collection. I'm kind of interested in the negative effects of fantasy - I guess relative to the number of fantasy games that exist, I don't own all that many. Similarly, I realized at some point in going over my collection that I actually don't have that many games with dice rolling.

```{r coefs mrbananagrabber, warning=F, message=F, fig.height=10, fig.width=11}
# for mrbananagrabber
plot_coef_function(training_coefs,
                   0.01,
                   "mrbananagrabber")

```

What about Quinns? Similar effects for number of mechanics mechanics, as that's pretty universal. He also has a Zman, Asmodee, Fantasy Flight positive effect, similar to me, which isn't surprising given that I probably follow his tastes more than anyone else. The Spies-Secret Agents effect is probably why we'll see a lot of hidden identity games that he likes show up. There are some interesting effects in there in the negatives - stock holding, simulation, dice rolling. It's interesting to me that he you see a negative effect for WWII, given that he loves the Undaunted series and Memoir 44, but again, relative to the number of WWII games that are out there, they compose a relatively small part of his collection.

```{r coefs Quinns, warning=F, message=F, fig.height=10, fig.width=11}

# for Quinns
plot_coef_function(training_coefs,
                   effect_size = 0.02,
                             "Quinns")

```

Rahdo might have the most easily understood tastes out of anyone here. Even before looking at the model, I know that he dislikes take that mechanics, conflict heavy and pick up and deliver games, and he generally only keeps games that play well with 2 players. And if we look at the model, we can see that show up: wargames, max players, min players, take that, bluffing, miniatures all negative. Rahdo's collection also skews more heavily towards recent games, so yearpublished has a pretty huge effect for him. He also likes a city of city building and economic games, so not too surprising to see those show up.

```{r coefs rahdo, warning=F, message=F, fig.height=10, fig.width=11}

# for rahdo
plot_coef_function(training_coefs,
                   effect_size = 0.05,
                   "rahdo")

```

I actually don't know Tom Vasel's tastes all that well. One thing I did notice, though, is that because he's been reviewing games for such a long time, his pile of previously owned games is massive. As a result, if you look at the 'have owned' effect for yearpublished, it's super negative, whereas his owned games is positive for yearpublished. 

```{r coefs tom vasel, warning=F, message=F, fig.height=10, fig.width=11}

# for TomVasel
plot_coef_function(training_coefs,
                   effect_size = 0.1,
                             "TomVasel")

```

Similar plots for Mark Bigney. Here's a guy who likes his Reiner Knizia and dislikes Games Workshop. He also has some pretty stark differences between his played and own models, as he generally plays a lot of games for his podcast that he doesn't go on to keep in his collection.

```{r coefs Gyges, warning=F, message=F, fig.height=10, fig.width=11}

# for Gyges
plot_coef_function(training_coefs,
                   effect_size = 0.05,
                             "Gyges")

```

Watch It Played. He only has games listed that he owns, and doesn't have ratings, so the models are all the same.

```{r coefs Watch_It_Played, warning=F, message=F, fig.height=10, fig.width=11}

# for Watch_It_Played
plot_coef_function(training_coefs,
                   effect_size = 0.05,
                             "Watch_It_Played")

```

ZeeGarcia

```{r coefs zee, warning=F, message=F, fig.height=10, fig.width=11}

# for ZeeGaarcia
plot_coef_function(training_coefs,
                   effect_size = 0.05,
                             "ZeeGarcia")
  
```




### Examining OOS Predictions

We can extract the predictions from resampling for the penalized models and the boosted trees for each reviewer.

```{r spread out and create flextable from own model}

# spread out by outcome
oos_preds = training_preds_glmnet = all_models %>%
  mutate(glmnet_results = map(glmnet_results, ~ .x %>%
                                mutate(outcome = as.character(outcome)) %>%
                                rename(outcome_char = outcome) %>%
                                arrange(.row))) %>%
  mutate(glmnet_preds = map(glmnet_fit,
                     ~ predict(.x, new_data = baked_train) %>%
                       as_tibble() %>%
                       mutate(.row = row_number()))) %>%
  mutate(glmnet_out = case_when(outcome_type == 'rating' ~ glmnet_preds,
                                TRUE ~ glmnet_results)) %>%
  select(username, outcome_type, glmnet_out) %>%
  unnest() %>%
  mutate(pred = case_when(outcome_type == 'rating' ~ .pred,
                          outcome_type == 'have_owned' ~ .pred_1,
                          outcome_type == 'have_played' ~ .pred_1,
                          outcome_type == 'own' ~ .pred_1))  %>%
  select(username, outcome_type, outcome_char, pred, .row) %>%
  left_join(., baked_train %>%
              mutate(.row = row_number()),
            by = ".row") %>%
  mutate(method = "glmnet")


# # spread out by outcome
# training_preds_xgbTree = all_models %>%
#   mutate(xgbTree_results = map(xgbTree_results, ~ .x %>%
#                                 mutate(outcome = as.character(outcome)) %>%
#                                 rename(outcome_char = outcome) %>%
#                                 arrange(.row))) %>%
#   mutate(xgbTree_preds = map(xgbTree_fit,
#                      ~ predict(.x, new_data = baked_train) %>%
#                        as_tibble() %>%
#                        mutate(.row = row_number()))) %>%
#   mutate(xgbTree_out = case_when(outcome_type == 'rating' ~ xgbTree_preds,
#                                 TRUE ~ xgbTree_results)) %>%
#   select(username, outcome_type, xgbTree_out) %>%
#   unnest() %>%
#   mutate(pred = case_when(outcome_type == 'rating' ~ .pred,
#                           outcome_type == 'have_owned' ~ .pred_1,
#                           outcome_type == 'own' ~ .pred_1))  %>%
#   select(username, outcome_type, outcome_char, pred, .row) %>%
#   left_join(., baked_train %>%
#               mutate(.row = row_number()),
#             by = ".row") %>%
#   mutate(method = "xgbTree")


```

Examine side by side for reviewers

```{r side by side for reviewers, warning=F, message=F}

col_func<- function(x) {
  
  breaks<-seq(0, 1, 0.01)
#  breaks = weight_deciles
  colorRamp=colorRampPalette(c("white", "deepskyblue1"))
  col_palette <- colorRamp(length(breaks))
  mycut <- cut(x, 
    breaks = breaks,
    include.lowest = TRUE, 
    right=T,
    label = FALSE)
  col_palette[mycut]
  
}


reviewer_table_function = function(preds,
                                   outcome) {
  
  # flextable for owned
  preds %>%
    filter(outcome_type == outcome) %>%
    select(username, outcome_type, method, pred, .row, game_id, name, yearpublished) %>%
    group_by(game_id, name) %>%
    mutate(mean = mean(pred),
           sd = sd(pred)) %>%
    group_by(username) %>%
    spread(username, pred) %>%
    mutate_if(is.numeric, round, 2) %>%
    arrange(desc(mean)) %>%
    select(-.row) %>%
    mutate(game_id = as.character(game_id),
           yearpublished = as.character(yearpublished)) %>%
    rename(Outcome = outcome_type,
           Method = method,
           Published = yearpublished,
           ID = game_id,
           Game = name,
           Mean = mean,
           mrbngr = mrbananagrabber,
        #   NoPunInc = NoPunIncluded,
           TomVas = TomVasel,
           ZeeGarc = ZeeGarcia,
           WtchItPly = Watch_It_Played,
           SD = sd
           ) %>%
    select(Method, Outcome, ID, Published, Game, Mean, SD, mrbngr, everything()) %>%
    head(25) %>%
    flextable() %>%
    flextable::autofit() %>%
    bg(., j = c("Mean", "Gyges", "mrbngr",
           #     "NoPunInc",
                "Quinns", "rahdo", "TomVas", "WtchItPly", "ZeeGarc"),
       bg = col_func) %>%
    set_caption(paste("Highest Pr(", paste(outcome), ") by Reviewer"))

  
}

# side by side for own, glmnet
reviewer_table_function(training_preds_glmnet,
                        'own')

# side by side for own, glmnet
reviewer_table_function(training_preds_glmnet,
                        'have_played')

# # side by side for own, xgbTree
# reviewer_table_function(training_preds_xgbTree,
#                         'own')

```

For individuals

```{r look at individuals in flextable, warning=F, message=F}

# function
individual_table_function <- function(preds, username) {
  
  # flextable for owned
  preds %>%
    filter(outcome_type == 'own' | outcome_type == 'have_played') %>%
    select(username, outcome_type, method, pred, .row, game_id, name, yearpublished) %>%
    group_by(game_id, name) %>%
    mutate(mean = mean(pred),
           sd = sd(pred)) %>%
    group_by(username)%>%
    spread(outcome_type, pred) %>%
    ungroup() %>%
    mutate_if(is.numeric, round, 2) %>%
    arrange(desc(mean)) %>%
    select(-.row) %>%
    mutate(game_id = as.character(game_id),
           yearpublished = as.character(yearpublished)) %>%
    rename(Username = username,
           Method = method,
           Published = yearpublished,
           ID = game_id,
           Game = name,
           Own = own,
       #   Owned = have_owned,
           Played = have_played
           ) %>%
    select(Method, ID, Published, Game, Username,
           Own, 
         #  Owned, 
           Played) %>%
    filter(Username == paste(username)) %>%
    arrange(desc(Own)) %>%
    head(25) %>%
    flextable() %>%
    flextable::autofit() %>%
    bg(., j = c("Own",
            #    "Owned",
                "Played"),
       bg = col_func) %>%
    set_caption(paste("Pr(Own) and Pr(Played) for ", paste(username), sep=""))

  
}

# me
individual_table_function(training_preds_glmnet,
                          "mrbananagrabber")

# rahdo
individual_table_function(training_preds_glmnet,
                          "rahdo")

# Quinns
individual_table_function(training_preds_glmnet,
                          "Quinns")

# Gyges
individual_table_function(training_preds_glmnet,
                          "Gyges")

# TomVasel
individual_table_function(training_preds_glmnet,
                          "TomVasel")

# TomVasel
individual_table_function(training_preds_glmnet,
                          "Watch_It_Played")

```

## Predicting Games Published 2020-2022

We can now use the resulting models to predict 2020 games.

```{r create 2020 set}

# combine all
games_test<-active_games %>%
  select(timestamp, game_id, name, average, baverage, usersrated) %>%
  left_join(., games_info %>% # join game info
              select(game_id, yearpublished, avgweight, minage, minplayers, maxplayers, playingtime),
            by = c("game_id")) %>%
  filter(yearpublished >= 2020) %>% # use games prior to 2020 as our training set
  left_join(., game_categories %>% # join categories
              mutate(category = gsub("\\)", "", gsub("\\(", "", category))) %>%
              mutate(category = tolower(paste("cat", gsub("[[:space:]]", "_", gsub("\\s+", " ", gsub("[[:punct:]]","", category))), sep="_"))) %>%
              mutate(has_category = 1) %>%
              select(-category_id) %>%
              pivot_wider(names_from = c("category"),
                          values_from = c("has_category"),
                          id_cols = c("game_id"),
                          names_sep = "_",
                          values_fn = min,
                          values_fill = 0),
            by = c("game_id")) %>%
  left_join(., game_mechanics %>% # join mechanics
              mutate(mechanic = tolower(paste("mech", gsub("[[:space:]]", "_", gsub("\\s+", " ", gsub("[[:punct:]]","", mechanic))), sep="_"))) %>%
              mutate(has_mechanic = 1) %>%
              select(-mechanic_id) %>%
              pivot_wider(names_from = c("mechanic"),
                          values_from = c("has_mechanic"),
                          id_cols = c("game_id"),
                          names_sep = "_",
                          values_fn = min,
                          values_fill = 0),
            by = c("game_id")) %>%
      left_join(., game_designers %>% # join designers
              mutate(designer = gsub("\\)", "", gsub("\\(", "", designer))) %>%
              mutate(designer = tolower(paste("des", gsub("[[:space:]]", "_", gsub("\\s+", " ", gsub("[[:punct:]]","", designer))), sep="_"))) %>%
              mutate(has_designer = 1) %>%
              select(-designer_id) %>%
              pivot_wider(names_from = c("designer"),
                          values_from = c("has_designer"),
                          id_cols = c("game_id"),
                          names_sep = "_",
                          values_fn = min,
                          values_fill = 0),
            by = c("game_id")) %>%
        left_join(., game_publishers %>% # join publishers
                          filter(publisher_id %in% publisher_list) %>%
              mutate(publisher = gsub("\\)", "", gsub("\\(", "", publisher))) %>%
              mutate(publisher = tolower(paste("pub", gsub("[[:space:]]", "_", gsub("\\s+", " ", gsub("[[:punct:]]","", publisher))), sep="_"))) %>%
              mutate(has_publisher = 1) %>%
              select(-publisher_id) %>%
              pivot_wider(names_from = c("publisher"),
                          values_from = c("has_publisher"),
                          id_cols = c("game_id"),
                          names_sep = "_",
                          values_fn = min,
                          values_fill = 0),
              by = c("game_id")) %>%
      left_join(., 
                game_collections %>%
                mutate(username = case_when(username == 'Watch%20It%20Played' ~ 'Watch_It_Played',
                                            TRUE ~ username)) %>%
                mutate(own = case_when(username == 'TomVasel' & rating >= 8 ~ 1,
                         TRUE ~ own)) %>%
                mutate(have_played = case_when(own == 1 | prevowned == 1 | !(is.na(rating)) ~ 1,
                                               TRUE ~ 0)) %>%
                mutate(have_owned = case_when(own == 1 | prevowned == 1 | (username == 'Quinns' & !is.na(rating)) ~ 1,
                                              TRUE ~ 0)) %>%
                select(game_id, own, have_owned, have_played, rating, username) %>%
                pivot_wider(names_from = c("username"),
                            values_from = c("own", "have_owned", "have_played", "rating"),
                            values_fn = max,
                            id_cols = game_id) %>%
                mutate_at(vars(starts_with("have_owned_")),
                         ~ replace_na(., 0)) %>%
                  mutate_at(vars(starts_with("own_")),
                         ~ replace_na(., 0)),
                mutate_at(vars(starts_with("have_played_")),
                         ~ replace_na(., 0)),
                by = c("game_id"))


```

Bake using our previous recipe, then predict.

```{r bake and predict}

baked_test = recipe_model %>%
  prep(games_train, strings_as_factor = F) %>%
  bake(games_test)

```

Now predict using the previously trained models.

```{r predict using models, warning=F}

test_probs = all_models  %>%
  filter(outcome_type != 'rating') %>%
  select(username, outcome_type, glmnet_fit) %>%
  #select(username, outcome_type, glmnet_fit, xgbTree_fit) %>%
  mutate(glmnet_preds = map(glmnet_fit,
                            ~ .x %>%
                              predict(baked_test, type = 'prob') %>%
                              rename(glmnet = .pred_1) %>%
                              select(glmnet) %>%
                              mutate(.row = row_number())))%>%
  # mutate(xgbTree_preds = map(xgbTree_fit,
  #                            ~ .x %>%
  #                              predict(baked_test, type = 'prob') %>%
  #                              rename(xgbTree = .pred_1) %>%
  #                              select(xgbTree) %>%
  #                              mutate(.row = row_number()))) %>%
  select(username, outcome_type, glmnet_preds) %>%
 # select(username, outcome_type, glmnet_preds, xgbTree_preds) %>%
  unnest() %>%
  select(-one_of(".row1")) %>%
  left_join(., baked_test %>%
              mutate(.row = row_number()),
            by = ".row") %>%
  mutate(user_variable = paste(outcome_type, username, sep="_"))
  
  
```

#### Evaluating 2020

We can now open these up and take a look. Let's do an evaluation on the 2020 games. Let's first establish a baseline logloss for each username.

```{r get baseline}

baked_train %>%
  select(yearpublished, game_id, name, starts_with("have_owned"), starts_with("own"), starts_with("have_played")) %>%
  filter(yearpublished > 2000) %>%
  melt(., id.vars = c("yearpublished", "game_id", "name")) %>%
  mutate(username = gsub("own_", "", gsub("have_played_", "", gsub("have_owned_", "", variable)))) %>%
  group_by(username) %>%
  mutate(outcome_type = gsub(paste("_", username, sep=""), "", variable)) %>%
  group_by(yearpublished, outcome_type, username) %>%
  summarize(prop = sum(value) / n()) %>%
  ggplot(., aes(x=yearpublished,
                color = username,
                y = prop,
                by = username))+
  geom_line(lwd=1.04)+
  facet_wrap(outcome_type~.,
             ncol = 3)+
  theme_phil()+
  scale_color_colorblind()+
  my_caption

baseline_probs = baked_train %>%
  select(yearpublished, game_id, name, starts_with("have_owned"), starts_with("own"), starts_with("have_played")) %>%
  melt(., id.vars = c("yearpublished", "game_id", "name")) %>%
  mutate(username = gsub("own_", "", gsub("have_played_", "", gsub("have_owned_", "", variable)))) %>%
  group_by(username) %>%
  mutate(outcome_type = gsub(paste("_", username, sep=""), "", variable)) %>%
  group_by(outcome_type, username) %>%
  summarize(prop = sum(value) / n()) %>%
  mutate_if(is.numeric, round, 3)

```


```{r test preds and actual}

test_probs_with_actual = test_probs %>%
  left_join(.,
    baked_test %>%
    select(yearpublished, game_id, name, starts_with("have_owned"), starts_with("own"), starts_with("have_played")) %>%
    melt(., id.vars = c("yearpublished", "game_id", "name")) %>%
    rename(user_variable = variable) %>%
    select(yearpublished, game_id, name, user_variable, value)) %>%
  select(yearpublished, username, outcome_type, .row, glmnet, value, name, game_id) %>%
  mutate(actual = factor(case_when(value == 0 ~ 'no',
                            TRUE ~ 'yes'))) %>%
  select(-value) %>%
  melt(id.vars=c("username", "outcome_type", ".row", "actual", "yearpublished", "name", "game_id"))

# roc, should be .5
test_probs_with_actual %>%
  group_by(username, outcome_type) %>%
  left_join(., baseline_probs) %>%
  yardstick::roc_auc(truth = actual,
                     estimate = prop,
                     event_level = "second")
# logloss
baseline_logloss = test_probs_with_actual %>%
  group_by(username, outcome_type) %>%
  left_join(., baseline_probs) %>%
  yardstick::mn_log_loss(truth = actual,
                     estimate = prop,
                     event_level = "second") %>%
  mutate_if(is.numeric, round, 3) %>%
  mutate(variable = "null") %>%
  select(variable, everything())

baseline_logloss

```


```{r evalaute 2020 preds, fig.height=8, fig.width=11}

test_probs_with_actual %>%
  filter(yearpublished == 2020) %>%
  group_by(username, outcome_type, variable) %>%
  yardstick::roc_auc(truth = actual,
                     estimate = value,
                     event_level = "second") %>%
  mutate_if(is.numeric, round, 3) %>%
  ggplot(., aes(x=reorder(username, .estimate),
                y = .estimate,
                color = outcome_type))+
  geom_point()+
  facet_wrap(variable+.metric~.)+
  theme_phil()+
  coord_flip(ylim = c(0.5, 0.9))+
  scale_color_colorblind()+
  xlab("")+
  my_caption


test_probs_with_actual %>%
  filter(yearpublished == 2020) %>%
  group_by(yearpublished, username, outcome_type, variable) %>%
  yardstick::roc_curve(truth = actual,
                     estimate = value,
                     event_level = "second") %>%
  ggplot(aes(x = 1 - specificity, y = sensitivity)) +
  geom_path(aes(by = username, 
                color = username)) +
  geom_abline(lty = 3) +
 # coord_equal() +
  theme_phil()+
  facet_wrap(yearpublished + outcome_type ~.,
             ncol = 3)+
  scale_color_colorblind()+
  my_caption

```

We can evaluate the logloss for our models compared to the null.

```{r compare, warning=F, message=F}

test_probs_with_actual %>%
  filter(yearpublished == 2020) %>%
  group_by(username, outcome_type, variable) %>%
  yardstick::mn_log_loss(truth = actual,
                     estimate = value,
                     event_level = "second") %>%
  bind_rows(baseline_logloss) %>%
  spread(variable, .estimate) %>%
  mutate_if(is.numeric, round, 3)

```

We can also calculate precision and recall.

```{r specify thresholds and compute, warning=F, message=F, fig.height=8, fig.width=11}

cuts = seq(0.01, 0.5, by = 0.01)

thresh_metrics = metric_set(yardstick::bal_accuracy,
                            yardstick::precision,
                            yardstick::recall,
                            yardstick::kap,
                            yardstick::mcc,
                            yardstick::f_meas)

output = foreach(i = 1:length(cuts), .combine = bind_rows) %do% {
  
  test_probs_with_actual %>%
  filter(yearpublished == 2020) %>%
  group_by(username, outcome_type, variable) %>%
  mutate(value = factor(case_when(value > cuts[i] ~ 'yes',
                           TRUE ~ 'no'))) %>%
  thresh_metrics(truth = actual,
                 estimate = value,
                 event_level = "second") %>%
    mutate(cut = cuts[i])
  
}

output %>%
  filter(outcome_type == 'own') %>%
  ggplot(., aes(x=cut,
                color = username,
                y=.estimate))+
  geom_line()+
  facet_wrap(outcome_type+.metric ~.,
             scales="free_y")+
  theme_phil()+
  scale_color_colorblind()

```

What maximizes the balanced accuracy for each username?

```{r check for balanced acc and f1}

output %>%
  filter(outcome_type == 'own') %>%
  filter(.metric == 'bal_accuracy' | .metric == 'f_meas') %>%
  group_by(username, .metric) %>%
  slice_max(.estimate)

```

Let's look at the games for 2020 each user is predicted to like/own.

```{r table of preds}

test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2020) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  select(-.row, -actual, -variable) %>%
  group_by(username) %>%
  spread(username, pred) %>%
  mutate(method = 'glmnet') %>%
  mutate_if(is.numeric, round, 2) %>%
     mutate(game_id = as.character(game_id),
           yearpublished = as.character(yearpublished)) %>%
    rename(Outcome = outcome_type,
           Method = method,
           Published = yearpublished,
           ID = game_id,
           Game = name,
           Mean = mean,
           mrbngr = mrbananagrabber,
          # NoPunInc = NoPunIncluded,
           TomVas = TomVasel,
           ZeeGarc = ZeeGarcia,
           WtchItPly = Watch_It_Played,
           SD = sd
           ) %>%
    select(Method, Outcome, ID, Published, Game, Mean, SD, mrbngr, everything()) %>%
  arrange(desc(Mean)) %>%
    head(25) %>%
    flextable() %>%
    flextable::autofit() %>%
    bg(., j = c("Mean", "Gyges", "mrbngr", 
              #  "NoPunInc",
                "Quinns", "rahdo", "TomVas", "WtchItPly", "ZeeGarc"),
       bg = col_func) %>%
          set_caption(paste("Highest Pr(Own) for Games Published in 2020"))


```

We can look at individual's top games for 2020, as well as whether they actually own them.

```{r individual 2020 with actual}

# rahdo
test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2020) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  filter(username == 'rahdo') %>%
  arrange(desc(pred)) %>%
  select(username,outcome_type, yearpublished, game_id, name, pred, actual) %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(yearpublished = as.character(yearpublished),
         game_id = as.character(game_id)) %>%
  ungroup() %>%
  mutate(rank = row_number()) %>%
  select(everything(), rank) %>%
  head(50) %>%
  flextable() %>%
  flextable::autofit() %>%
  bg(., i = ~ actual == 'yes',
     bg = 'deepskyblue1') %>%
          set_caption(paste("Highest Pr(Own) for Games Published in 2020"))


# quinns
test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2020) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  filter(username == 'Quinns') %>%
  arrange(desc(pred)) %>%
  select(username,outcome_type, yearpublished, game_id, name, pred, actual) %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(yearpublished = as.character(yearpublished),
         game_id = as.character(game_id)) %>%
  ungroup() %>%
  head(50) %>%
  mutate(rank = row_number()) %>%
  select(everything(), rank) %>%
  flextable() %>%
  flextable::autofit() %>%
  bg(., i = ~ actual == 'yes',
     bg = 'deepskyblue1') %>%
          set_caption(paste("Highest Pr(Own) for Games Published in 2020"))


# TomVasel
test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2020) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  filter(username == 'TomVasel') %>%
  arrange(desc(pred)) %>%
  select(username,outcome_type, yearpublished, game_id, name, pred, actual) %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(yearpublished = as.character(yearpublished),
         game_id = as.character(game_id)) %>%
  ungroup() %>%
  mutate(rank = row_number()) %>%
  select(everything(), rank) %>%
  head(50) %>%
  flextable() %>%
  flextable::autofit() %>%
  bg(., i = ~ actual == 'yes',
     bg = 'deepskyblue1') %>%
          set_caption(paste("Highest Pr(Own) for Games Published in 2020"))


# Gyges
test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2020) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  filter(username == 'Gyges') %>%
  arrange(desc(pred)) %>%
  select(username,outcome_type, yearpublished, game_id, name, pred, actual) %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(yearpublished = as.character(yearpublished),
         game_id = as.character(game_id)) %>%
  ungroup() %>%
  mutate(rank = row_number()) %>%
  select(everything(), rank) %>%
  head(50) %>%
  flextable() %>%
  flextable::autofit() %>%
  bg(., i = ~ actual == 'yes',
     bg = 'deepskyblue1') %>%
          set_caption(paste("Highest Pr(Own) for Games Published in 2020"))

# Zee
test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2020) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  filter(username == 'ZeeGarcia') %>%
  arrange(desc(pred)) %>%
  select(username,outcome_type, yearpublished, game_id, name, pred, actual) %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(yearpublished = as.character(yearpublished),
         game_id = as.character(game_id)) %>%
  ungroup() %>%
  mutate(rank = row_number()) %>%
  select(everything(), rank) %>%
  head(50) %>%
  flextable() %>%
  flextable::autofit() %>%
  bg(., i = ~ actual == 'yes',
     bg = 'deepskyblue1') %>%
          set_caption(paste("Highest Pr(Own) for Games Published in 2020"))

# mrbananagrabber
test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2020) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  filter(username == 'mrbananagrabber') %>%
  arrange(desc(pred)) %>%
  select(username,outcome_type, yearpublished, game_id, name, pred, actual) %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(yearpublished = as.character(yearpublished),
         game_id = as.character(game_id)) %>%
  ungroup() %>%
  mutate(rank = row_number()) %>%
  select(everything(), rank) %>%
  head(50) %>%
  flextable() %>%
  flextable::autofit() %>%
  bg(., i = ~ actual == 'yes',
     bg = 'deepskyblue1') %>%
          set_caption(paste("Highest Pr(Own) for Games Published in 2020"))

  
# Watch_It_Played
test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2020) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  filter(username == 'Watch_It_Played') %>%
  arrange(desc(pred)) %>%
  select(username,outcome_type, yearpublished, game_id, name, pred, actual) %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(yearpublished = as.character(yearpublished),
         game_id = as.character(game_id)) %>%
  ungroup() %>%
  mutate(rank = row_number()) %>%
  select(everything(), rank) %>%
  head(50) %>%
  flextable() %>%
  flextable::autofit() %>%
  bg(., i = ~ actual == 'yes',
     bg = 'deepskyblue1') %>%
          set_caption(paste("Highest Pr(Own) for Games Published in 2020"))

```

#### Predicting 2021

And now 2021.

```{r 2020 own}

test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2021) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  select(-.row, -actual, -variable) %>%
  group_by(username) %>%
  spread(username, pred) %>%
  mutate(method = 'glmnet') %>%
  mutate_if(is.numeric, round, 2) %>%
     mutate(game_id = as.character(game_id),
           yearpublished = as.character(yearpublished)) %>%
    rename(Outcome = outcome_type,
           Method = method,
           Published = yearpublished,
           ID = game_id,
           Game = name,
           Mean = mean,
           mrbngr = mrbananagrabber,
          # NoPunInc = NoPunIncluded,
           TomVas = TomVasel,
           ZeeGarc = ZeeGarcia,
           WtchItPly = Watch_It_Played,
           SD = sd
           ) %>%
    select(Method, Outcome, ID, Published, Game, Mean, SD, mrbngr, everything()) %>%
  arrange(desc(Mean)) %>%
    head(25) %>%
    flextable() %>%
    flextable::autofit() %>%
    bg(., j = c("Mean", "Gyges", "mrbngr", 
              #  "NoPunInc",
                "Quinns", "rahdo", "TomVas", "WtchItPly", "ZeeGarc"),
       bg = col_func) %>%
        set_caption(paste("Highest Pr(Own) by Reviewer for Games Published in 2021"))


```

Ugh stupid Long Shot.

```{r what is the deal with long shot}

bind_rows(baked_train,
           baked_test) %>% 
   filter(yearpublished > 2000) %>%
   mutate(label = case_when(number_mechanics > 10 ~ name,
                            TRUE ~ NA_character_)) %>%
   mutate(col = case_when(name == 'Long Shot: The Dice Game' ~ 'yes',
                          TRUE ~ 'no')) %>%
   ggplot(., aes(x=number_mechanics,
                 label = label,
            #     size = col,
                 color = col,
                 y = yearpublished))+
   geom_text(check_overlap = T,
             size = 3,
            position=position_jitter(width=0.2,height=0.2))+
   geom_jitter(alpha=0.5)+
   theme_phil()+
   guides(label = "none",
          color = "none",
          size = "none")+
   scale_color_manual(values = c("grey60", "darkred"))+
  my_caption


```

We can look at individuals for 2021

```{r individual 2021 with actual}

# rahdo
test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2021) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  filter(username == 'rahdo') %>%
  arrange(desc(pred)) %>%
  select(username,outcome_type, yearpublished, game_id, name, pred, actual) %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(yearpublished = as.character(yearpublished),
         game_id = as.character(game_id)) %>%
  ungroup() %>%
  mutate(rank = row_number()) %>%
  select(everything(), rank) %>% 
  head(50) %>%
  flextable() %>%
  flextable::autofit() %>%
  bg(., i = ~ actual == 'yes',
     bg = 'deepskyblue1')

# quinns
test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2021) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  filter(username == 'Quinns') %>%
  arrange(desc(pred)) %>%
  select(username,outcome_type, yearpublished, game_id, name, pred, actual) %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(yearpublished = as.character(yearpublished),
         game_id = as.character(game_id)) %>%
  ungroup() %>%
  mutate(rank = row_number()) %>%
  select(everything(), rank) %>%
  head(50) %>%
  flextable() %>%
  flextable::autofit() %>%
  bg(., i = ~ actual == 'yes',
     bg = 'deepskyblue1')

# TomVasel
test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2021) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  filter(username == 'TomVasel') %>%
  arrange(desc(pred)) %>%
  select(username,outcome_type, yearpublished, game_id, name, pred, actual) %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(yearpublished = as.character(yearpublished),
         game_id = as.character(game_id)) %>%
  ungroup() %>%
  mutate(rank = row_number()) %>%
  select(everything(), rank) %>%
  head(50) %>%
  flextable() %>%
  flextable::autofit() %>%
  bg(., i = ~ actual == 'yes',
     bg = 'deepskyblue1')

# Gyges
test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2021) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  filter(username == 'Gyges') %>%
  arrange(desc(pred)) %>%
  select(username,outcome_type, yearpublished, game_id, name, pred, actual) %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(yearpublished = as.character(yearpublished),
         game_id = as.character(game_id)) %>%
  ungroup() %>%
  mutate(rank = row_number()) %>%
  select(everything(), rank) %>%
  head(50) %>%
  flextable() %>%
  flextable::autofit() %>%
  bg(., i = ~ actual == 'yes',
     bg = 'deepskyblue1')

# mrbananagrabber
test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2021) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  filter(username == 'mrbananagrabber') %>%
  arrange(desc(pred)) %>%
  select(username,outcome_type, yearpublished, game_id, name, pred, actual) %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(yearpublished = as.character(yearpublished),
         game_id = as.character(game_id)) %>%
  ungroup() %>%
  mutate(rank = row_number()) %>%
  select(everything(), rank) %>%
  head(50) %>%
  flextable() %>%
  flextable::autofit() %>%
  bg(., i = ~ actual == 'yes',
     bg = 'deepskyblue1')
  
# Watch_It_Played
test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2021) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  filter(username == 'Watch_It_Played') %>%
  arrange(desc(pred)) %>%
  select(username,outcome_type, yearpublished, game_id, name, pred, actual) %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(yearpublished = as.character(yearpublished),
         game_id = as.character(game_id)) %>%
  ungroup() %>%
  mutate(rank = row_number()) %>%
  select(everything(), rank) %>%
  head(50) %>%
  flextable() %>%
  flextable::autofit() %>%
  bg(., i = ~ actual == 'yes',
     bg = 'deepskyblue1')

# ZeeGarcia
test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2021) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  filter(username == 'ZeeGarcia') %>%
  arrange(desc(pred)) %>%
  select(username,outcome_type, yearpublished, game_id, name, pred, actual) %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(yearpublished = as.character(yearpublished),
         game_id = as.character(game_id)) %>%
  ungroup() %>%
  mutate(rank = row_number()) %>%
  select(everything(), rank) %>%
  head(50) %>%
  flextable() %>%
  flextable::autofit() %>%
  bg(., i = ~ actual == 'yes',
     bg = 'deepskyblue1')
  

```

#### Predicting 2022

And 2022

```{r now 2022}

test_probs_with_actual %>%
  filter(outcome_type == 'own') %>%
  filter(yearpublished == 2022) %>%
  group_by(game_id, name) %>%
  rename(pred = value) %>%
  mutate(mean = mean(pred),
           sd = sd(pred)) %>%
  select(-.row, -actual, -variable) %>%
  group_by(username) %>%
  spread(username, pred) %>%
  mutate(method = 'glmnet') %>%
  mutate_if(is.numeric, round, 2) %>%
     mutate(game_id = as.character(game_id),
           yearpublished = as.character(yearpublished)) %>%
    rename(Outcome = outcome_type,
           Method = method,
           Published = yearpublished,
           ID = game_id,
           Game = name,
           Mean = mean,
           mrbngr = mrbananagrabber,
          # NoPunInc = NoPunIncluded,
           TomVas = TomVasel,
           ZeeGarc = ZeeGarcia,
           WtchItPly = Watch_It_Played,
           SD = sd
           ) %>%
    select(Method, Outcome, ID, Published, Game, Mean, SD, mrbngr, everything()) %>%
  arrange(desc(Mean)) %>%
    head(50) %>%
    flextable() %>%
    flextable::autofit() %>%
    bg(., j = c("Mean", "Gyges", "mrbngr", 
              #  "NoPunInc",
                "Quinns", "rahdo", "TomVas", "WtchItPly", "ZeeGarc"),
       bg = col_func) %>%
      set_caption(paste("Highest Pr(Own) by Reviewer for Games Published in 2022"))

```

## Predicting Individual Games

Weather Machine

```{r weather machine, warning=F, message=F}

source("functions/get_game_record.R")

# load
id = 237179

# get the game
raw_record = get_game_record(237179)

# attach all names from training
record = bind_rows(raw_record,
                   games_train[0,])

# bake using previously trained recipe
baked_record = recipe_model %>%
  prep(games_train, strings_as_factor = F) %>%
  bake(record)
         

# predict
pred_record = all_models %>%
  filter(outcome_type != 'rating') %>%
  select(username, outcome_type, glmnet_fit) %>%
  #select(username, outcome_type, glmnet_fit, xgbTree_fit) %>%
  mutate(glmnet_preds = map(glmnet_fit,
                            ~ .x %>%
                              predict(baked_record, type = 'prob') %>%
                              rename(glmnet = .pred_1) %>%
                              select(glmnet) %>%
                              mutate(.row = row_number()))) %>%
  # mutate(xgbTree_preds = map(xgbTree_fit,
  #                            ~ .x %>%
  #                              predict(baked_test, type = 'prob') %>%
  #                              rename(xgbTree = .pred_1) %>%
  #                              select(xgbTree) %>%
  #                              mutate(.row = row_number()))) %>%
  select(username, outcome_type, glmnet_preds) %>%
 # select(username, outcome_type, glmnet_preds, xgbTree_preds) %>%
  unnest() %>%
  select(-one_of(".row1")) %>%
  left_join(., baked_record %>%
              mutate(.row = row_number()),
            by = ".row") 

# now look at the prediction
pred_record %>%
  filter(outcome_type == 'own' | outcome_type == 'have_played') %>%
  select(game_id, yearpublished, game_id, name, username, glmnet, outcome_type) %>%
  mutate(method = "glmnet") %>%
  spread(outcome_type, glmnet) %>%
  mutate(game_id = as.character(game_id),
         yearpublished = as.character(yearpublished)) %>%
  rename(Method = method,
         Published = yearpublished,
         ID = game_id,
         Game = name,
         User = username) %>%
  rename(`Pr(Own)` = own,
         `Pr(Play)` = have_played) %>%
  arrange(desc(`Pr(Own)`)) %>%
    select(Method, Published, ID, Game, User, `Pr(Own)`, `Pr(Play)`) %>%
      mutate_if(is.numeric, round, 2) %>%
    flextable() %>%
    bg(., j = c("`Pr(Own)`", "`Pr(Play)`"),
       bg = col_func)


```

Lords of Ragnarok

```{r lords of ragnarak, warning=F, message=F}

# load
id =340865

# get the game
raw_record = get_game_record(id)

# attach all names from training
record = bind_rows(raw_record,
                   games_train[0,])

# bake using previously trained recipe
baked_record = recipe_model %>%
  prep(games_train, strings_as_factor = F) %>%
  bake(record)
         

# predict
pred_record = all_models %>%
  filter(outcome_type != 'rating') %>%
  select(username, outcome_type, glmnet_fit) %>%
  #select(username, outcome_type, glmnet_fit, xgbTree_fit) %>%
  mutate(glmnet_preds = map(glmnet_fit,
                            ~ .x %>%
                              predict(baked_record, type = 'prob') %>%
                              rename(glmnet = .pred_1) %>%
                              select(glmnet) %>%
                              mutate(.row = row_number()))) %>%
  # mutate(xgbTree_preds = map(xgbTree_fit,
  #                            ~ .x %>%
  #                              predict(baked_test, type = 'prob') %>%
  #                              rename(xgbTree = .pred_1) %>%
  #                              select(xgbTree) %>%
  #                              mutate(.row = row_number()))) %>%
  select(username, outcome_type, glmnet_preds) %>%
 # select(username, outcome_type, glmnet_preds, xgbTree_preds) %>%
  unnest() %>%
  select(-one_of(".row1")) %>%
  left_join(., baked_record %>%
              mutate(.row = row_number()),
            by = ".row") 
  

# now look at the prediction
pred_record %>%
  filter(outcome_type == 'own' | outcome_type == 'have_played') %>%
  select(game_id, yearpublished, game_id, name, username, glmnet, outcome_type) %>%
  mutate(method = "glmnet") %>%
  spread(outcome_type, glmnet) %>%
  mutate(game_id = as.character(game_id),
         yearpublished = as.character(yearpublished)) %>%
  rename(Method = method,
         Published = yearpublished,
         ID = game_id,
         Game = name,
         User = username) %>%
  rename(`Pr(Own)` = own,
         `Pr(Play)` = have_played) %>%
  arrange(desc(`Pr(Own)`)) %>%
    select(Method, Published, ID, Game, User, `Pr(Own)`, `Pr(Play)`) %>%
      mutate_if(is.numeric, round, 2) %>%
    flextable() %>%
    flextable::autofit() %>%
    bg(., j = c("`Pr(Own)`", "`Pr(Play)`"),
       bg = col_func)

```

Ark Nova

```{r ark nova, warning=F, message=F}

# load
id =342942

# get the game
raw_record = get_game_record(id)

# attach all names from training
record = bind_rows(raw_record,
                   games_train[0,])

# bake using previously trained recipe
baked_record = recipe_model %>%
  prep(games_train, strings_as_factor = F) %>%
  bake(record)
         

# predict
pred_record = all_models %>%
  filter(outcome_type != 'rating') %>%
  select(username, outcome_type, glmnet_fit) %>%
  #select(username, outcome_type, glmnet_fit, xgbTree_fit) %>%
  mutate(glmnet_preds = map(glmnet_fit,
                            ~ .x %>%
                              predict(baked_record, type = 'prob') %>%
                              rename(glmnet = .pred_1) %>%
                              select(glmnet) %>%
                              mutate(.row = row_number()))) %>%
  # mutate(xgbTree_preds = map(xgbTree_fit,
  #                            ~ .x %>%
  #                              predict(baked_test, type = 'prob') %>%
  #                              rename(xgbTree = .pred_1) %>%
  #                              select(xgbTree) %>%
  #                              mutate(.row = row_number()))) %>%
  select(username, outcome_type, glmnet_preds) %>%
 # select(username, outcome_type, glmnet_preds, xgbTree_preds) %>%
  unnest() %>%
  select(-one_of(".row1")) %>%
  left_join(., baked_record %>%
              mutate(.row = row_number()),
            by = ".row") 
  

# now look at the prediction
pred_record %>%
  filter(outcome_type == 'own' | outcome_type == 'have_played') %>%
  select(game_id, yearpublished, game_id, name, username, glmnet, outcome_type) %>%
  mutate(method = "glmnet") %>%
  spread(outcome_type, glmnet) %>%
  mutate(game_id = as.character(game_id),
         yearpublished = as.character(yearpublished)) %>%
  rename(Method = method,
         Published = yearpublished,
         ID = game_id,
         Game = name,
         User = username) %>%
  rename(`Pr(Own)` = own,
         `Pr(Play)` = have_played) %>%
  arrange(desc(`Pr(Own)`)) %>%
    select(Method, Published, ID, Game, User, `Pr(Own)`, `Pr(Play)`) %>%
      mutate_if(is.numeric, round, 2) %>%
    flextable() %>%
    flextable::autofit() %>%
    bg(., j = c("`Pr(Own)`", "`Pr(Play)`"),
       bg = col_func)

```

Imperial Steam

```{r imperial steam, warning=F}
id = 338760

# get the game
raw_record = get_game_record(id)

# attach all names from training
record = bind_rows(raw_record,
                   games_train[0,])

# bake using previously trained recipe
baked_record = recipe_model %>%
  prep(games_train, strings_as_factor = F) %>%
  bake(record)
         

# predict
pred_record = all_models %>%
  filter(outcome_type != 'rating') %>%
  select(username, outcome_type, glmnet_fit) %>%
  #select(username, outcome_type, glmnet_fit, xgbTree_fit) %>%
  mutate(glmnet_preds = map(glmnet_fit,
                            ~ .x %>%
                              predict(baked_record, type = 'prob') %>%
                              rename(glmnet = .pred_1) %>%
                              select(glmnet) %>%
                              mutate(.row = row_number()))) %>%
  # mutate(xgbTree_preds = map(xgbTree_fit,
  #                            ~ .x %>%
  #                              predict(baked_test, type = 'prob') %>%
  #                              rename(xgbTree = .pred_1) %>%
  #                              select(xgbTree) %>%
  #                              mutate(.row = row_number()))) %>%
  select(username, outcome_type, glmnet_preds) %>%
 # select(username, outcome_type, glmnet_preds, xgbTree_preds) %>%
  unnest() %>%
  select(-one_of(".row1")) %>%
  left_join(., baked_record %>%
              mutate(.row = row_number()),
            by = ".row") 
  

# now look at the prediction
pred_record %>%
  filter(outcome_type == 'own' | outcome_type == 'have_played') %>%
  select(game_id, yearpublished, game_id, name, username, glmnet, outcome_type) %>%
  mutate(method = "glmnet") %>%
  spread(outcome_type, glmnet) %>%
  mutate(game_id = as.character(game_id),
         yearpublished = as.character(yearpublished)) %>%
  rename(Method = method,
         Published = yearpublished,
         ID = game_id,
         Game = name,
         User = username) %>%
  rename(`Pr(Own)` = own,
         `Pr(Play)` = have_played) %>%
  arrange(desc(`Pr(Own)`)) %>%
    select(Method, Published, ID, Game, User, `Pr(Own)`, `Pr(Play)`) %>%
      mutate_if(is.numeric, round, 2) %>%
    flextable() %>%
    flextable::autofit() %>%
    bg(., j = c("`Pr(Own)`", "`Pr(Play)`"),
       bg = col_func)


```

Tomorrow Dies Today

```{r tomorrow dies today, warning=F}
id = 305498

# get the game
raw_record = get_game_record(id)

# attach all names from training
record = bind_rows(raw_record,
                   games_train[0,])

# bake using previously trained recipe
baked_record = recipe_model %>%
  prep(games_train, strings_as_factor = F) %>%
  bake(record)
         

# predict
pred_record = all_models %>%
  filter(outcome_type != 'rating') %>%
  select(username, outcome_type, glmnet_fit) %>%
  #select(username, outcome_type, glmnet_fit, xgbTree_fit) %>%
  mutate(glmnet_preds = map(glmnet_fit,
                            ~ .x %>%
                              predict(baked_record, type = 'prob') %>%
                              rename(glmnet = .pred_1) %>%
                              select(glmnet) %>%
                              mutate(.row = row_number()))) %>%
  # mutate(xgbTree_preds = map(xgbTree_fit,
  #                            ~ .x %>%
  #                              predict(baked_test, type = 'prob') %>%
  #                              rename(xgbTree = .pred_1) %>%
  #                              select(xgbTree) %>%
  #                              mutate(.row = row_number()))) %>%
  select(username, outcome_type, glmnet_preds) %>%
 # select(username, outcome_type, glmnet_preds, xgbTree_preds) %>%
  unnest() %>%
  select(-one_of(".row1")) %>%
  left_join(., baked_record %>%
              mutate(.row = row_number()),
            by = ".row") 
  

# now look at the prediction
pred_record %>%
  filter(outcome_type == 'own' | outcome_type == 'have_played') %>%
  select(game_id, yearpublished, game_id, name, username, glmnet, outcome_type) %>%
  mutate(method = "glmnet") %>%
  spread(outcome_type, glmnet) %>%
  mutate(game_id = as.character(game_id),
         yearpublished = as.character(yearpublished)) %>%
  rename(Method = method,
         Published = yearpublished,
         ID = game_id,
         Game = name,
         User = username) %>%
  rename(`Pr(Own)` = own,
         `Pr(Play)` = have_played) %>%
  arrange(desc(`Pr(Own)`)) %>%
    select(Method, Published, ID, Game, User, `Pr(Own)`, `Pr(Play)`) %>%
      mutate_if(is.numeric, round, 2) %>%
    flextable() %>%
    flextable::autofit() %>%
    bg(., j = c("`Pr(Own)`", "`Pr(Play)`"),
       bg = col_func)


```

## Save Output

```{r save outputs}

# save training preds
save(oos_preds, file = paste("reviewer_predictions_data/oos_preds_", Sys.Date(), ".csv", sep=""))

# save test preds
save(test_probs, file = paste("reviewer_predictions_data/test_preds_", Sys.Date(), ".csv", sep=""))

```



```

